%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% thesis.tex — Carbon Lock-in or Circular Transition?
%% Heterogeneity in Japan's Waste Incineration Fleet
%% and Net-Zero Compatibility
%% Compilable with: pdflatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,a4paper]{article}

%% ---------- packages ----------
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage{xurl}
\usepackage[round]{natbib}
\usepackage{setspace}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array}

% Right-aligned and centered tabularx column types
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}

\onehalfspacing
\setlength{\emergencystretch}{2em}

%% ---------- title information ----------
\title{%
  Carbon Lock-in or Circular Transition?\\
  Heterogeneity in Japan's Waste Incineration Fleet\\
  and Net-Zero Compatibility%
}
\author{Pann Phetra \\ Student ID: 13223029 \\ Supervisor: Prof. Han Ji \\ Ritsumeikan Asia Pacific University}
\date{2026}

%% ==========================================================
\begin{document}
\maketitle

%% ==========================================================
%% ABSTRACT
%% ==========================================================
\begin{abstract}
Japan's waste incinerators are not all the same, and that heterogeneity determines whether incineration helps or hurts the country's carbon goals. Using a 20-year facility-level panel of 23,599 observations across 2,948 incinerators (Ministry of the Environment, FY2005--2024), this thesis separates two questions that are often conflated: which coded facilities first observed without generation make an observed transition into power generation, and conditional on power generation, which facility characteristics predict energy recovery efficiency.

Three findings stand out. First, observed transition on the extensive margin is selective rather than diffuse. In the coded full-fleet panel, 141 observed first-adoption events occur among 2,035 facilities first observed without power generation, and 109 of those events occur between FY2013 and FY2019. In the lagged adoption hazard, facilities older than 10 years in the prior observed year are about 1.5--2.2 percentage points less likely than facilities aged 0--10 years to transition into power generation in the current year, while each additional 100 t/day of prior-year design capacity raises annual transition probability by about 1.5 percentage points. Second, conditional on power generation, facility age exerts a consistent and substantial negative effect on efficiency: coefficients range from roughly $-0.025$ to $-0.043$ across the robustness specifications ($p < 0.001$ throughout), and mean efficiency declines from 0.400 MWh/t at facilities aged 0--10 years to 0.183 MWh/t at facilities over 30 years old. Scale is a strong positive predictor, and capacity utilization is similarly strong, with coefficients in the 0.54--0.78 range across the main specifications. Third, within-facility efficiency in the canonical generator regression frame is still dominated by between-facility differences: the within-to-total variation ratio is 0.1499, falling to 0.0956 in the post-Fukushima window. This descriptive pattern is strongly consistent with infrastructure lock-in and bounded within-facility responsiveness among generators.

At the fleet level, consolidation has reduced facility count from 1,318 to 1,014 ($-23\%$) between 2005 and 2024, while the share of power-generating facilities has nearly doubled from 21.6\% to 41.1\%. Yet 59\% of active facilities still generate no electricity. Gross avoided CO$_2$ emissions from waste-to-energy reached approximately 4.6 million t-CO$_2$ in FY2024 (an upper bound excluding process emissions from combustion), but this aggregate masks profound heterogeneity: a small number of large, modern facilities account for most of the benefit.

These results reframe the policy challenge. Fleet-wide improvement depends heavily on capital-side modernization decisions, while the generator-only analysis shows that operating performance then responds within a bounded design envelope rather than through large within-facility shifts over time. The thesis therefore concludes that observed transition into power generation is concentrated among younger and larger facilities, not diffused evenly across old small plants, and that net-zero compatibility depends on accelerating capital-side modernization while preserving routing, utilization, and selective major-refurbishment levers as secondary tools.
\end{abstract}

\noindent\textbf{Keywords:} waste-to-energy, energy recovery efficiency, carbon lock-in, industrial ecology, Japan, fleet heterogeneity, infrastructure transition

\newpage
\tableofcontents
\newpage

%% ==========================================================
%% CHAPTER 1: INTRODUCTION
%% ==========================================================

\section{Introduction}

\subsection{The Paradox of Japan's Incineration Infrastructure}

Every day, Japan burns roughly 90,000 tonnes of municipal solid waste. This is not an anomaly or a failure of recycling policy; it is the deliberate architecture of the world's most incineration-dependent waste management system, built over decades in a country where landfill space is scarce, geography is mountainous, and population density is extreme \citep{MOEJ2022}. Japan's incinerators are not temporary solutions awaiting replacement by something cleaner. They are permanent infrastructure, embedded in local government budgets, staffed by long-term employees, and serving as the physical backbone of urban metabolism in hundreds of municipalities.

And yet Japan has committed to carbon neutrality by 2050. This commitment creates a tension that has received insufficient analytical attention: the country's waste sector, which contributes meaningfully to national greenhouse gas emissions, is anchored by a fleet of over 1,000 facilities with lifespans typically exceeding 30 years. The question is not whether Japan will eventually decarbonize its waste system. The question is which facilities can contribute to that transition, and which cannot, and what determines the difference.

This thesis addresses that question through the lens of \emph{energy recovery efficiency}: the amount of electricity generated per tonne of waste processed. Among Japan's incinerators, this metric varies dramatically. Some modern facilities generate nearly 0.5 MWh per tonne, comparable to small-scale renewable energy installations in terms of carbon avoided. Others, the majority, generate nothing at all, burning waste with no attempt to recover its thermal energy. Between these extremes lies a heterogeneous fleet whose carbon implications depend critically on which segment grows, which stagnates, and which is retired.

\subsection{Background: Japan's Waste-to-Energy System}

Japan's commitment to incineration dates to the 1960s, when rapid urbanization combined with severe land constraints made landfilling politically and physically untenable in most of the country \citep{TabataTsai2016}. The national government provided subsidies for municipal incinerators, and local authorities responded by building them at scale. By the early 2000s, Japan operated more than 1,300 general waste incineration facilities, more than any other nation, and the system had become deeply institutionalized \citep{MOEJ2022}.

The technical core of these facilities is a \emph{stoker grate furnace} (a mechanically driven combustion bed that moves waste through the burn zone), supplemented in more modern installations by heat recovery boilers and steam turbines that convert thermal energy into electricity. This conversion, from waste combustion to electrical output, is what transforms an incinerator into a \emph{waste-to-energy} (WtE) facility. Not all Japanese incinerators make this conversion. Many, particularly older ones, simply burn waste and release heat to the atmosphere.

The energy recovery story has changed over time. In 2005, only about 21.6\% of Japan's operating incinerators generated any electricity. By 2024, that share had risen to 41.1\%, a substantial increase, achieved partly through new construction and partly through retirement of non-generating facilities. Over the same period, total facility count fell from 1,318 to 1,014. The fleet is shrinking and modernizing simultaneously, but 59\% of active facilities still produce no power, a striking persistence given two decades of energy policy evolution.

This trajectory intersects with two major structural shocks. The first is the 2011 Fukushima Daiichi nuclear disaster, which caused Japan to shut down virtually all of its nuclear generating capacity and scrambled national energy markets. In this context, distributed power sources, including waste-to-energy, gained renewed policy attention as Japan sought to replace lost baseload capacity with a diversified portfolio \citep{SasakawaPF2012}. The second is the Paris Agreement commitments of 2015 and Japan's subsequent Green Growth Strategy, which set the 2050 carbon neutrality target and prompted systematic review of emission sources across all sectors, including waste.

\subsection{The Problem: Heterogeneity Without Accountability}

Despite this policy backdrop, Japan's incineration fleet has not been systematically analyzed through a heterogeneity lens. Most existing research treats WtE facilities as a category, comparing Japan to other countries, modeling aggregate emission flows, or evaluating specific technologies in isolation. What has been missing is a facility-level account of \emph{what distinguishes high-efficiency from low-efficiency facilities}, and whether these distinctions are stable over time or responsive to operational and policy variables.

This gap matters for two reasons. First, aggregate statistics obscure the distribution. A fleet average efficiency of 0.30 MWh/t could represent a uniformly mediocre system or a bimodal distribution of excellent and poor performers. These scenarios have entirely different policy implications: the former calls for universal technology upgrades, while the latter calls for selective retirement and consolidation. Second, the fleet-level transition into power generation and the conditional efficiency of already-generating facilities are analytically distinct. If modernization occurs mainly through the entry of large new plants while efficiency within existing generators changes only modestly, then policy must work through the investment and decommissioning cycle rather than through operational incentives alone.

The industrial ecology literature has developed concepts precisely for this kind of problem. \emph{Infrastructure lock-in} describes the phenomenon whereby early investment decisions constrain future options through physical durability, sunk costs, and co-evolutionary institutional arrangements \citep{Unruh2000}. \emph{Carbon lock-in} is the specific case where fossil fuel-intensive infrastructure persists beyond its economic or environmental optimum because the system of production, regulation, and social expectation surrounding it resists change \citep{Unruh2000}. Applied to waste incineration, lock-in predicts that low-efficiency facilities will continue operating not because they are optimal but because the institutional and physical architecture of local waste management makes replacing them costly and politically difficult.

Whether Japan's fleet is experiencing carbon lock-in, circular transition, or some heterogeneous combination of both; this is the empirical question this thesis addresses.

\subsection{Research Question and Objectives}

The primary research question guiding this thesis is:

\begin{quote}
\textbf{What predicts observed transition into power generation among coded facilities first seen without it, and conditional on power generation, what predicts energy recovery efficiency among power-generating incinerators?}
\end{quote}

To answer this, the thesis pursues four specific objectives:

\begin{enumerate}
  \item \textbf{Describe fleet evolution}: document how the composition, scale, and power-generation penetration of Japan's incineration fleet has changed between FY2005 and FY2024.
  \item \textbf{Identify modernization at the extensive margin}: estimate which facilities first adopt power generation within the observation window, using the coded full-fleet panel.
  \item \textbf{Identify efficiency determinants at the intensive margin}: estimate the effects of facility age, design capacity, capacity utilization, waste heating value, and regional grid emission factors on energy recovery efficiency among operating power-generating facilities, using panel regression with cluster-robust inference.
  \item \textbf{Assess bounded responsiveness and policy implications}: determine whether efficiency changes meaningfully within generators over time, or remains constrained by design vintage, and translate the two-part evidence into recommendations consistent with Japan's net-zero trajectory.
\end{enumerate}

\subsection{Significance of the Study}

This study makes three contributions. Analytically, it provides the first systematic multi-year facility-level analysis of Japan's incineration fleet that separates the extensive margin of power-generation adoption from the intensive margin of generator efficiency, using data from the Ministry of the Environment's General Waste Treatment Survey. Most prior empirical work on WtE efficiency has relied on cross-sectional comparisons or technology-level analyses; this two-part panel approach allows the thesis to distinguish fleet modernization from conditional operating performance.

Theoretically, the study applies infrastructure lock-in theory, developed primarily in the context of energy systems, to the waste sector, contributing to industrial ecology's understanding of how material metabolism infrastructure evolves and resists change. The adoption results show that observed transition into power generation is concentrated among younger and larger facilities in the coded risk set, while the generator-only results show that within-facility efficiency changes relatively little over time, with a within-facility variation ratio of 0.1499 in the canonical regression frame and a lower ratio still in the post-Fukushima period. Together these findings are strongly consistent with a sector in which capital-side modernization matters more than large late-life performance reversals within existing plants, while not by themselves identifying irreversibility or distinguishing retrofit from replacement or new build at the same site.

Policy-practically, the results arrive at a moment when Japan is actively restructuring its waste management system. The ongoing implementation of the Fundamental Plan for Establishing a Sound Material-Cycle Society, the framework that has organised Japanese waste policy around the 3Rs (reduce, reuse, recycle) since the early 2000s \citep{Sakai2011}, continues to emphasise consolidation of the incineration fleet and increased energy recovery alongside Japan's broader 2050 carbon-neutrality commitment \citep{MOEJ2024}. This thesis provides an evidence base for evaluating those policies: the extensive-margin evidence shows that power-generation adoption is already concentrated in large and young facilities, while the intensive-margin evidence shows that routing and utilization improvements matter mainly within the already-generating segment. The combination implies that consolidation and replacement remain the highest-leverage fleet-level interventions.

\subsection{Thesis Structure}

The remainder of this thesis is organized as follows. Chapter 2 reviews the relevant literature, covering the institutional context of Japan's WtE sector, the industrial ecology concepts of lock-in and material metabolism, the empirical literature on modernization and efficiency determinants, and the gap this study addresses. Chapter 3 describes the data, variable construction, two-part panel design, and estimation strategy. Chapter 4 presents the results: descriptive fleet trends, an extensive-margin adoption model, the generator-efficiency estimates across four main specifications and eight robustness specifications, and the avoided emissions calculation. Chapter 5 discusses what the results mean for theory and policy, including the relationship between modernization and bounded within-facility responsiveness. Chapter 6 concludes with a summary of contributions, policy recommendations, and directions for future research.

A note on framing: throughout this thesis, facilities with no power generation capability are not treated as nuisance observations outside the empirical design. They enter the extensive-margin adoption analysis and the descriptive fleet-composition sections. The generator-efficiency regressions are then explicitly conditional on positive power generation and positive operating output, because the dependent variable requires a meaningful positive value. This distinction, between the margin on which facilities adopt generation and the margin on which generators differ in efficiency, is central to the design of the study.

%% ==========================================================
%% CHAPTER 2: LITERATURE REVIEW
%% ==========================================================

\section{Literature Review}

\subsection{Overview}

This chapter situates the thesis within four bodies of literature. Section 2.2 reviews the institutional and technical development of Japan's waste-to-energy sector. Section 2.3 introduces the industrial ecology concepts of material metabolism and infrastructure lock-in that frame the analysis. Section 2.4 surveys the empirical literature on energy recovery efficiency determinants in WtE systems globally and in Japan. Section 2.5 identifies the gap, the absence of fleet-level heterogeneity analysis using multi-year panel data, that this study addresses.

\subsection{Japan's Waste-to-Energy System: Institutional Development and Technical Evolution}

\subsubsection{The Historical Foundation}

Japan's reliance on waste incineration is not accidental. The country combines high population density, mountainous terrain that limits landfill siting, and a cultural and regulatory emphasis on hygiene and waste containment that made open dumping politically unacceptable from a relatively early period of industrialization \citep{Tanikawa2015}. The Waste Disposal and Public Cleansing Law of 1970 established national frameworks for municipal waste management and accelerated the shift toward controlled thermal treatment \citep{TabataTsai2016}. By the 1980s, Japan had constructed incinerators at a pace that left no comparable national fleet anywhere in the world.

The financial architecture of this expansion is important to understand because it shapes the lock-in dynamics analyzed in later chapters. Municipal incinerators in Japan are overwhelmingly publicly owned and operated, or operated under long-term contracts by private firms on behalf of municipalities. Construction is heavily subsidized by national government grants, typically covering 25--50\% of capital costs \citep{TabataTsai2016}. Operating costs are borne by local governments, which creates a strong fiscal incentive to fully utilize installed capacity, a dynamic that, as this thesis demonstrates, has important implications for efficiency. The combination of high capital subsidy and municipal operational responsibility creates an institutional structure in which facilities, once built, are rarely closed early.

\subsubsection{Technical Architecture: From Thermal Treatment to Energy Recovery}

The dominant combustion technology in Japan's fleet is the \emph{stoker furnace} (also called a moving-grate furnace), in which waste is fed onto a mechanically driven grate that moves material through progressive combustion zones \citep{Niessen2010}. Stoker furnaces are favored for their ability to handle heterogeneous waste streams without preprocessing, their operational reliability, and their long operational track record. Alternatives, including \emph{fluidized bed combustors} (which suspend waste particles in an upward air current for more uniform combustion) and gasification systems, represent a small fraction of the Japanese fleet.

Energy recovery from combustion involves routing exhaust gases through a waste heat boiler to produce steam, which drives a turbine-generator set. The efficiency of this conversion depends on several factors: the steam temperature and pressure achievable, which are functions of furnace design and the metallurgical limits imposed by corrosive combustion gases; the turbine efficiency; and the extent to which parasitic electrical loads within the facility reduce net output. Larger facilities can justify higher-pressure boiler systems and more sophisticated turbine configurations, creating the scale economies that the regression analysis in this thesis detects; empirical work on Japan's fleet has found the same scale-to-recovery relationship at the national level \citep{Niessen2010, Sun2018}. Older facilities, designed to earlier engineering standards, cannot be straightforwardly upgraded to achieve modern performance levels because the boiler and turbine systems are integral to the structural design of the building.

\subsubsection{Policy Context: Energy and Climate Drivers}

Two policy developments frame the period analyzed in this thesis. First, Japan's Renewable Portfolio Standard (enacted under the 2002 Special Measures Law Concerning the Use of New Energy by Electric Utilities, effective April 2003) and its successor Feed-in Tariff (FiT) system made waste-derived electricity a revenue source that could offset operating costs, providing a direct incentive for municipalities to add or expand power generation at incineration facilities \citep{MOEJ2022}. The FiT introduced in 2012, following the Fukushima disaster, included waste-to-energy at rates that varied by facility type and scale.

Second, the 2015 Paris Agreement and Japan's Nationally Determined Contribution (NDC) commitments set increasingly stringent targets for economy-wide emissions reductions. Waste management contributes to Japan's greenhouse gas inventory through methane emissions from landfills, process CO$_2$ from combustion of biogenic and fossil fractions of waste, and the avoided emissions credited when waste-derived electricity displaces grid power \citep{MOEJ2024}. The net climate impact of incineration depends critically on the efficiency of energy recovery, precisely the variable this thesis examines.

The 2050 carbon neutrality target, formalized in Japan's Green Growth Strategy (2020) and subsequent policy documents, has intensified scrutiny of the waste sector. The government's approach has been to encourage consolidation, fewer, larger, more efficient facilities, rather than to mandate specific technology upgrades. This strategy is implicitly validated by the findings of this thesis, though the pace of consolidation observed in the data suggests it is proceeding more slowly than net-zero targets may require.

\subsubsection{Fleet Modernization and Consolidation}

The empirical literature on Japan's fleet trajectory is largely descriptive. Studies by the Ministry of the Environment's research institutes have documented the decline in facility count and the increase in power-generating share, but without multivariate analysis of what distinguishes modernizing from stagnating portions of the fleet \citep{MOEJ2022}. Aggregate statistics show that total incineration capacity has remained relatively stable even as facility count has fallen, consistent with a consolidation trend in which small old facilities are replaced by fewer large new ones.

International comparisons are instructive. Northern European countries, particularly Sweden, Denmark, and Germany, operate WtE fleets with substantially higher average energy recovery efficiencies than Japan, attributable to a combination of larger average facility size, district heating integration that allows recovery of both electricity and heat, and more recent construction vintage \citep{Munster2010}. Japan's very limited district heating network coverage, largely restricted to a handful of Hokkaido cities such as Sapporo and absent from most of the major population centers further south, means that only electrical efficiency is typically considered, understating the potential thermal recovery value but also limiting the realistic efficiency ceiling \citep{TabataTsai2016}.

\subsection{Industrial Ecology: Material Metabolism and Infrastructure Lock-In}

\subsubsection{Material Metabolism as Analytical Framework}

Industrial ecology approaches waste management as a question of material flows through social-technical systems, the ``metabolism'' of industrial society, by analogy with biological metabolism \citep{Ayres1994}. In this framing, incineration facilities are nodes in a material flow network: they receive organic and inorganic waste, transform it through combustion, and export energy, bottom ash, and air emissions. The efficiency of this transformation, how much useful energy is extracted per unit of material processed, is a direct measure of the metabolic productivity of the node.

The material metabolism perspective draws attention to system-level properties that facility-level analysis might miss. A single high-efficiency facility embedded in a network of low-efficiency facilities may have limited system-level impact if waste routing decisions are driven by proximity rather than efficiency. Conversely, consolidation of waste flows toward high-efficiency nodes is a system-level intervention that requires institutional coordination beyond the technical capacity of individual facilities. This perspective shapes the policy discussion in Chapter 5, where the fleet-level implications of the regression findings are developed.

\subsubsection{Infrastructure Lock-In: Mechanisms and Applications}

\emph{Lock-in}, in the industrial ecology literature, refers to the persistence of suboptimal technological trajectories due to the co-evolutionary entrenchment of physical infrastructure, institutions, and social practices \citep{Unruh2000}. The concept has roots in evolutionary economics, particularly \citet{Arthur1989}'s analysis of path dependence in technology adoption, but has been developed in the sustainability transitions literature to explain why sociotechnical systems resist change even when superior alternatives are available \citep{Geels2004}.

\emph{Carbon lock-in} is the specific case where energy and material systems dependent on fossil carbon persist beyond their economic or environmental optimum. \citet{Unruh2000} identifies three interacting mechanisms: technological lock-in (existing infrastructure embodies past design choices and is costly to abandon), institutional lock-in (regulatory frameworks, subsidy structures, and market rules co-evolve with dominant technologies), and cognitive lock-in (professional expertise, organizational routines, and public expectations are adapted to existing technology). All three mechanisms are visible in Japan's incineration sector: physical facilities with 30-year lifespans embody 1980s and 1990s engineering; municipal waste management governance is organized around existing facility locations; and the expertise of the waste management workforce is calibrated to stoker furnace operation.

\citet{Seto2016}, reviewing the lock-in literature fifteen years after Unruh's original formulation, distinguish three levels at which the mechanism operates, infrastructural, institutional, and behavioural, and argue that empirical progress has been hampered by the absence of facility-level tests. They define infrastructural lock-in specifically as the condition under which asset performance fails to respond to changing external incentives, and they call explicitly for empirical studies that operationalise this definition at the level of individual facilities rather than at the aggregate sectoral scale at which lock-in is usually discussed. This thesis provides exactly such a test: a 20-year facility-level panel of Japan's incinerator fleet is a setting in which external incentives changed dramatically (the 2011 Fukushima shock, the 2012 feed-in tariff, the 2023 net-zero policy revision) while the physical fleet remained largely the same, and the empirical question is whether facility-level performance responded.

The lock-in hypothesis has a specific empirical prediction for this study: if efficiency is primarily determined by design decisions made at construction, then the within-facility variance in efficiency over time should be low, much lower than the between-facility variance driven by differences in construction vintage and design capacity. This prediction is tested directly in the panel regression analysis. The result, a within-to-total variation ratio of 0.1499 in the canonical regression frame (0.1795 pre-Fukushima and 0.0956 post-Fukushima), provides clear support for the lock-in mechanism: most efficiency variation is between facilities, not within them over time.

\subsubsection{Circular Economy and Circular Transition}

Alongside the lock-in literature sits the growing body of work on circular economy and \emph{circular transition}, the reorganization of material flows to eliminate waste and maintain the value of materials and energy in use \citep{EllenMacArthur2013}. In the waste management context, circular economy thinking prioritizes material recovery (recycling, reuse) over energy recovery (incineration with power generation), which in turn is preferred over simple disposal (landfilling or combustion without energy recovery).

This hierarchy creates an apparent tension with WtE: by converting materials to energy, incineration forecloses material recovery options. However, the industrial ecology literature increasingly treats WtE not as an alternative to circular economy but as an element of an integrated system that handles residual waste streams that cannot be economically recycled \citep{Astrup2015}. In this view, the question is not whether to incinerate but how efficiently to recover energy from the incineration that will inevitably occur. The ``circular transition'' concept, as used in this thesis, refers specifically to the shift from non-energy-recovering incineration toward high-efficiency WtE, a transition that is clearly underway in Japan but far from complete.

\subsubsection{Stranded Assets and Infrastructure Transition}

A third conceptual thread from the industrial ecology and sustainability transitions literature concerns \emph{stranded assets}, infrastructure that loses value before the end of its physical or economic life because of shifts in the regulatory, technological, or market environment \citep{Caldecott2016}. In the context of this thesis, the stranded asset risk applies to two types of facilities: old low-efficiency power-generating incinerators that are unlikely to improve their performance before retirement, and non-power-generating facilities that may face political pressure to add generation capacity they are too old or too small to accommodate economically.

The stranded asset concept connects to the net-zero policy discussion because it highlights the cost dimension of transition. A municipality that built a new incinerator in 2000 faces a very different calculus from one that built in 1985: the former facility may have 15 years of remaining service life and be young enough to justify retrofitting or efficiency improvements; the latter may be approaching end of life in any case. The regression finding that age is the single most consistent predictor of efficiency, with effects ranging from $-0.028$ to $-0.043$ per year, means that the stranded asset risk is spatially distributed across Japan according to the vintage of local infrastructure, creating a heterogeneous transition challenge.

\subsection{Determinants of Energy Recovery Efficiency: The Empirical Literature}

\subsubsection{Scale Effects}

The relationship between facility scale and energy recovery efficiency is among the most consistently documented findings in the WtE literature. Larger facilities can support higher-pressure boiler systems, more sophisticated turbine configurations, better instrumentation and control, and more specialized technical staff, all of which contribute to higher electricity output per tonne of waste \citep{Genon2008}. Scale economies in boiler design are particularly significant: at small scale, heat losses relative to output are large, and the pressure ratings achievable are limited by the cost of pressure vessel fabrication. At large scale, fixed costs are amortized over more output and engineering can be optimized.

This relationship has been documented empirically in European contexts, where WtE facilities range from small municipal installations to very large urban facilities exceeding 1,000 tonnes per day of capacity. Studies of the Danish and German fleets find positive and statistically significant relationships between facility capacity and electrical efficiency \citep{Munster2010}. The current study extends this finding to Japan's fleet, where the scale range is similarly large, from facilities below 50 t/day to installations exceeding 500 t/day, and where the policy relevance of the scale relationship is directly tied to the consolidation agenda.

\subsubsection{Facility Age and Vintage Effects}

Age effects in WtE efficiency have been analyzed less systematically than scale effects, partly because most empirical studies use cross-sectional data that conflate age with design vintage. A facility built in 1985 operates with 1985 engineering standards regardless of how many years have passed; its low efficiency reflects design constraints, not degradation. This distinction between age-as-proxy-for-vintage and age-as-wear-and-tear is important but often blurred in the literature.

Some studies have examined facility degradation, the decline in performance of boiler systems and turbines as they age, finding modest efficiency losses that are partially offset by maintenance and component replacement \citep{Astrup2015}. However, the more robust finding across multiple contexts is that the vintage effect (newer facilities are built to more efficient designs) dominates the degradation effect. This is consistent with the lock-in hypothesis: design determines efficiency, and design improves with each generation of new construction.

The Japanese context adds a specific dimension: the rapid expansion of the fleet in the 1980s and 1990s means that a large cohort of facilities share a similar vintage and will reach end of life within a relatively compressed time window. This creates both a challenge (managing a wave of simultaneous retirements) and an opportunity (replacing them with modern, efficient facilities on a planned schedule).

\subsubsection{Capacity Utilization}

Capacity utilization, the ratio of actual throughput to design capacity, affects efficiency through thermodynamic and operational mechanisms. At low utilization, combustion systems operate outside their design range, making it difficult to maintain stable temperatures and steam parameters. Below certain throughput thresholds, facilities may switch from power-generating mode to simple heat disposal mode to maintain combustion stability. High utilization, conversely, allows facilities to operate at or near design conditions, maximizing steam generation and turbine output.

The empirical literature on utilization effects in WtE is sparse but generally consistent with a positive relationship \citep{Beylot2015}. The policy implication, that routing more waste to high-utilization facilities improves system-level efficiency, points toward regional consolidation as a policy lever. In Japan's highly fragmented waste management system, where municipal jurisdiction boundaries often limit inter-municipality waste transfers, this implication is institutionally challenging to implement even where the technical case is clear.

\subsubsection{Waste Composition and Heating Value}

The energy content of waste, typically measured as lower heating value (LHV) in MJ/kg, is a natural candidate for an efficiency determinant. Higher-energy waste should, all else equal, generate more steam per unit mass, and hence more electricity. However, the empirical literature on this relationship is surprisingly ambiguous \citep{Astrup2009}.

Several mechanisms complicate the straightforward prediction. First, modern furnace control systems are designed to maintain stable combustion temperatures across a range of waste heating values, effectively buffering the direct relationship between waste energy content and boiler output. Second, high-heating-value waste may require additional cooling (through waste mixing or steam injection) to prevent equipment damage, reducing net efficiency gains. Third, the heating value data available in administrative datasets, typically estimated from waste composition surveys rather than direct measurement, may not accurately reflect actual combustion conditions.

This thesis finds that heating value is not a statistically significant predictor of efficiency in any of the main or robustness specifications, a result that aligns with the more skeptical strand of the literature and has important implications for data collection policy.

\subsubsection{Regional and Grid Factors}

Some studies include regional variables to capture differences in grid emission factors, energy prices, or climate conditions that might affect operational decisions. The theoretical case for a grid emission factor effect on \emph{efficiency} (as opposed to \emph{avoided emissions}) is not straightforward, a facility's efficiency in converting waste to electricity should not depend on what that electricity displaces in the grid. However, there may be indirect effects through incentive structures: in regions with high grid emission factors, the value of waste-derived electricity is higher, potentially incentivizing investment in efficiency upgrades or attracting more capital to new facility construction.

This thesis includes regional grid emission factors as a control variable and finds that the coefficient sign is unstable across model specifications, positive in some and negative in others, suggesting that this variable does not capture a stable efficiency determinant. This instability is itself informative: it suggests that regional energy market conditions are not a reliable lever for improving incineration efficiency, and that the primary determinants are physical (age, scale) rather than economic.

\subsection{The Research Gap: Fleet-Level Heterogeneity Analysis}

The literature surveyed above shares a common limitation: it treats WtE efficiency determinants as properties of technology types or average systems, rather than as characteristics that vary systematically across a heterogeneous fleet over time. Cross-sectional studies capture between-facility variation at a point in time but cannot assess whether the relationships are stable, how they change as the fleet modernizes, or what within-facility dynamics look like over time. Technology-level analyses abstract from the facility-level variation that is, empirically, the main source of efficiency differences in the Japanese fleet.

Three gaps are particularly important. First, no published study has applied panel regression methods to Japan's full incineration fleet using facility-level administrative data over a multi-decade period. The available data source, the Ministry of the Environment's General Waste Treatment Survey, covers all operating facilities annually and contains the variables needed for this analysis, but it has not been exploited for this purpose in the academic literature. Second, the question of within-facility efficiency dynamics, whether facilities improve their performance over their operational lives, has not been addressed empirically for Japan. This question is theoretically central to the lock-in debate: if within-facility improvement is negligible, then operational optimization policies are ineffective and retirement/replacement is the only viable path. Third, the fleet-level implications of heterogeneity, the distribution of avoided emissions across facility types, the concentration of efficiency gains in a small number of large modern plants, have not been quantified.

This thesis addresses all three gaps. It contributes a panel dataset of 23,599 facility-year observations, regression estimates robust to multiple model specifications, and a framework for translating fleet heterogeneity findings into net-zero policy recommendations grounded in industrial ecology theory.

%% ==========================================================
%% CHAPTER 3: METHODOLOGY
%% ==========================================================

\section{Methodology}

\subsection{Overview}

This chapter describes the data, variable construction, sample selection, and estimation strategy used to answer the research question. The empirical design has two linked parts. The first explains modernization on the extensive margin, which facilities first adopt power generation within the observation window. The second explains cross-facility variation in energy recovery efficiency conditional on adoption. The methodological challenge is to keep those two margins distinct while still drawing coherent conclusions about the fleet.

The chapter proceeds as follows. Section 3.2 describes the data source and its structure. Section 3.3 explains the cleaning and panel construction steps. Section 3.4 defines the dependent and independent variables. Section 3.5 describes the two-part estimation strategy and the rationale for model selection. Section 3.6 details the robustness checks for the generator-efficiency models.

\subsection{Data Source}

\subsubsection{The General Waste Treatment Survey}

The primary data source is the Ministry of the Environment (MOE) General Waste Treatment Survey (\emph{Ippan Haikibutsu Shori Jittai Chosa}), an annual administrative survey covering all operating general waste treatment facilities in Japan. The survey collects facility-level data on waste input volumes, treatment method, facility capacity, operational status, and, for energy-recovering facilities, electricity generation and fuel consumption. The survey has been conducted annually since the 1960s in various forms; the analysis in this thesis uses the fiscal year (FY) 2005 through FY2024 editions, covering 20 years of fleet evolution \citep{MOEJ2022}. The FY2005 start date is chosen deliberately: Japan's Air Pollution Control Law and Waste Management Law dioxin-emission standards, enacted in 1999 and phased in through the early 2000s, triggered a wave of retrofits, closures, and replacements that only stabilised around the middle of the decade. Starting in FY2005 ensures that the fleet under analysis operates under a stable regulatory regime for dioxin and fine-particulate emissions throughout the observation window, so that the estimated age and capacity effects are not confounded with a compliance-driven restructuring episode.

The survey is conducted by prefectural governments, which collect data from individual municipalities, which in turn collect from individual facilities. This administrative chain means the data are subject to reporting conventions that vary somewhat across prefectures and years. The cleaning process described in Section 3.3 addresses the most significant of these inconsistencies.

The appeal of the General Waste Treatment Survey for this research is threefold. First, it is near-census in coverage: because facility operation requires permits under the Waste Disposal Law and because municipal expenditure on waste management is reported to the national government, there is strong incentive for accurate and complete reporting. Second, it contains the specific variables needed for this analysis, waste volume, facility capacity, electricity generation, and facility age, at the facility level over multiple years. Third, it is publicly available, making the analysis replicable by other researchers and policy analysts.

\subsubsection{Panel Structure}

The raw dataset, after merging annual survey files for FY2005--FY2024, contains observations at the facility-year level. Not all facilities appear in all years, both because of entries (new facilities beginning operation) and exits (facility closures). This creates an unbalanced panel, a structure in which different facilities contribute different numbers of years of data.

The full panel contains 23,599 facility-year observations across 2,948 unique facilities. The average facility contributes 8.0 years of data, though this varies substantially: some facilities appear in all 20 years, while others appear for only one or two years, typically corresponding to opening or closure years in which full-year data are not available. After restricting to observations with an official facility code present, the coded full-fleet frame used for the extensive-margin analysis contains 19,827 observations across the same 2,948 facilities.

\subsection{Data Cleaning and Panel Construction}

\subsubsection{Facility Identification and Linking}

The most significant data quality challenge in working with the General Waste Treatment Survey is facility identification across years. Official facility codes are present for most, but not all, observations. The canonical analysis therefore takes a conservative approach: both the extensive-margin adoption model and the generator-efficiency panel use only observations with an official facility code present when constructing panel identifiers and clustering standard errors, while retaining the larger uncoded set for high-level descriptive counts. The resulting attrition is documented explicitly in the analysis sample report generated by the pipeline rather than being absorbed silently through ad hoc filtering.

Municipal mergers (\emph{heisei no daigappei}, the wave of municipal consolidations that reduced Japan's municipality count from approximately 3,200 to 1,700, peaking in 2004--2006 with tail-end mergers extending into the early 2010s \citep{Rausch2006}) create particular challenges because facilities may be reported under different administrative units before and after merger without any change in physical characteristics. These cases were identified and corrected manually where possible.

\subsubsection{Variable Cleaning and Outlier Treatment}

Several variables required cleaning before analysis. Facility age is floored at zero for a small number of one-year commissioning mismatches. For the extensive-margin model, the coded full-fleet panel is converted into an observed first-adoption risk set: facilities already generating power in their first observed year are treated as left-censored and excluded from the adoption hazard, while facilities first observed without power generation remain in the risk set until they either adopt generation or leave the panel. This yields 13,770 facility-year observations across 2,035 facilities, with 141 observed first-adoption events and 913 left-censored facilities already generating in their first observed year. The adoption model itself is estimated on a smaller lagged frame of 11,717 facility-year observations across 1,915 facilities and 140 events, because the first observed at-risk year for each facility has no lagged predictors and 18 additional rows lack prior-year age or capacity values.

Waste input volume and electricity generation are reported in absolute units (tonnes and kWh, respectively) that must be combined to compute efficiency. Observations with non-positive waste input or non-positive electricity output are excluded from the operating power-generation sample used for descriptive and regression analysis. Capacity utilization is capped at 1.0 at analysis time to prevent emergency-overload years from dominating the coefficient scale.

The efficiency variable (electricity generation divided by waste input, in MWh per tonne) is winsorized by clipping to fixed engineering bounds of [0.01, 0.80] MWh/t. In the canonical generator regression frame, the dependent variable is therefore defined on power-generating observations with positive throughput, positive electricity output, an official facility code present, and all model covariates observed. This yields a final regression sample of 5,683 facility-year observations across 1,016 facilities.

The choice of 0.80 MWh/t as the upper winsorizing bound reflects the physical limits of WtE electricity generation: the theoretical maximum conversion efficiency of a stoker furnace system, at realistic waste heating values, is approximately 0.9--1.0 MWh/t, and values above 0.80 almost certainly reflect reporting inconsistencies rather than genuine performance. The lower bound of 0.01 MWh/t captures minimal but real power generation, excluding only observations that are effectively zero.

\subsubsection{Heating Value Estimation}

Waste heating value is not directly reported in the General Waste Treatment Survey. For some years and facilities, it can be estimated from supplementary survey data on waste composition; for others, it must be inferred from national or regional composition averages. Given the known limitations of this approach, the indirect measurement introduces substantial noise, heating value should be treated as an approximate control variable rather than a precisely measured independent variable. The finding that heating value is statistically insignificant in all model specifications may partly reflect this measurement noise, though the thermodynamic arguments for insignificance (Section 2.4.4) suggest genuine ambiguity.

\subsection{Variable Definitions}

\subsubsection{Dependent Variables}

The thesis uses two dependent variables aligned with the two empirical margins of interest.

\textbf{Extensive margin: first adoption of power generation.} The adoption outcome equals 1 in the fiscal year a facility is first observed with power-generation capability, conditional on having been observed without power generation in all prior years of the panel, and 0 otherwise. The extensive-margin model is therefore an observed first-adoption hazard estimated on the coded full-fleet risk set.

\textbf{Intensive margin: energy recovery efficiency conditional on generation.} The second dependent variable is the natural logarithm of energy recovery efficiency, defined as:

\begin{equation}
\text{log\_efficiency}_{it} = \ln\!\left(\frac{\text{Electricity generated}_{it} \text{ (MWh)}}{\text{Waste processed}_{it} \text{ (tonnes)}}\right)
\end{equation}

The log transformation serves two purposes. First, it addresses the right-skewed distribution of raw efficiency values, a small number of high-performing facilities pull the distribution rightward, and the log transformation produces a more symmetric distribution better suited to linear regression. Second, it yields coefficients interpretable as approximate proportional effects: a coefficient of $-0.028$ on facility age means that each additional year of age is associated with approximately a 2.8\% lower efficiency level. Robustness checks using the raw (untransformed) dependent variable are reported in Section 4.5.

\subsubsection{Independent Variables}

\textbf{Facility age} is measured as the number of years since the facility began operation as of the observation year. This is derived from the facility's reported start date and the fiscal year of each observation. Age is the primary variable of interest, motivated by the lock-in hypothesis that efficiency is determined by design vintage.

\textbf{Design capacity} is measured in tonnes per day (t/day) as reported in the survey. This reflects the facility's rated processing capacity, not its actual throughput. To facilitate interpretation, capacity is included in units of 100 t/day, so that the regression coefficient represents the efficiency gain associated with 100 additional t/day of design capacity.

    \textbf{Capacity utilization} is defined as the ratio of actual annual waste input to theoretical maximum annual input (design capacity $\times$ 365 days), expressed as a proportion. This variable captures how intensively a facility is operated relative to its design specification. It is bounded between 0 and 1 in theory, though values slightly above 1.0 are possible when facilities accept emergency waste transfers beyond design capacity; such observations are capped at 1.0 in the analysis frame.

\textbf{Waste heating value} is the estimated lower heating value of the waste stream processed, measured in MJ/kg. As noted above, this variable is estimated rather than directly measured and should be treated with appropriate caution.

\textbf{Grid emission factor} captures the carbon intensity of the regional electricity grid, measured in kg-CO$_2$/kWh. This variable varies across Japan's nine major regional electricity utility service areas and changes over time, particularly following the Fukushima-induced nuclear shutdowns and subsequent restructuring. It enters the model as a proxy for the value of waste-derived electricity generation in carbon terms and for regional energy market conditions.

\subsubsection{Summary Statistics}

\begin{table}[H]
  \centering
  \caption{Summary Statistics, Canonical Regression Frame ($n = 5{,}683$)}
  \label{tab:summary_stats}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l*{5}{r}@{}}
    \toprule
    Variable & Mean & SD & Min & Median & Max \\
    \midrule
    Efficiency (MWh/t)                     & 0.330    & 0.149 & 0.010    & 0.332    & 0.800    \\
    log(efficiency)                        & $-1.265$ & 0.675 & $-4.605$ & $-1.102$ & $-0.223$ \\
    Facility age (years)                   & 15.0     & 9.6   & 0        & 15       & 47       \\
    Design capacity (t/day)                & 330.9    & 226.2 & 20       & 280      & 1{,}800  \\
    Capacity utilization                   & 0.600    & 0.135 & 0.013    & 0.610    & 1.00     \\
    Heating value (MJ/kg)                  & 7.9      & 4.3   & 0.0      & 8.3      & 158.9    \\
    Grid emission factor (kg-CO$_2$/kWh)   & 0.458    & 0.088 & 0.282    & 0.453    & 0.860    \\
    \bottomrule
  \end{tabular*}
  \smallskip
  \begin{minipage}{\textwidth}
    \footnotesize\emph{Note:} The efficiency min (0.010) and max (0.800) coincide with the winsorising bounds described in Section~3.3.2. The heating-value field is retained as a noisy administrative control variable rather than interpreted as a clean engineering measurement.
  \end{minipage}
\end{table}

The mean efficiency of 0.330 MWh/t in the canonical generator sample is notably higher than the fleet-wide average (which would be lower still if non-generating facilities were assigned zero efficiency). The standard deviation of 0.149 MWh/t reflects substantial dispersion, and the interquartile range runs roughly from 0.21 to 0.38 MWh/t, confirming that heterogeneity in performance is large enough to motivate systematic analysis.

\subsection{Estimation Strategy}

\subsubsection{Two-Part Estimation Framework}

The empirical design separates the extensive margin of modernization from the intensive margin of generator performance.

\textbf{Extensive margin: adoption hazard.} The first-adoption model is:

\begin{equation}
\text{AdoptPower}_{it} = \alpha + \delta_1\,\text{AgeBand}_{i,t-1} + \delta_2\,\text{Capacity}_{i,t-1} + \lambda_p + \gamma_t + u_{it}
\end{equation}

where $\text{AdoptPower}_{it}$ equals 1 if facility $i$ is first observed adopting power generation in fiscal year $t$, $\lambda_p$ is a prefecture fixed effect, and $\gamma_t$ is a year fixed effect. The predictors are lagged one observed year so the adoption coefficients are read as pre-transition correlates rather than same-year redesign attributes. The main table reports a linear probability specification with standard errors clustered at facility level for percentage-point interpretation, while a discrete-time logit with the same lagged covariates is used as a robustness check and returns the same sign pattern. Age is entered in bands rather than linearly because the event rates are sharply nonlinear across the facility life cycle.

\textbf{Intensive margin: generator-efficiency panel.} Conditional on generation, the baseline estimating equation is:

\begin{equation}
\begin{aligned}
\ln(\text{efficiency}_{it}) ={} & \alpha + \beta_1\,\text{Age}_{it} + \beta_2\,\text{Capacity}_{it} + \beta_3\,\text{Utilization}_{it} \\
                                & + \beta_4\,\text{HeatingValue}_{it} + \beta_5\,\text{GridEF}_{it} + \gamma_t + \epsilon_{it}
\end{aligned}
\end{equation}

where $i$ indexes facilities, $t$ indexes fiscal years, $\gamma_t$ is a year fixed effect capturing common shocks (e.g., the Fukushima event, changes in the feed-in tariff), and $\epsilon_{it}$ is the idiosyncratic error term. Model 1 (pooled OLS) imposes $\gamma_t = 0$ for all $t$, so the year fixed effects drop out; Models 2 and 4 estimate $\gamma_t$ as a full set of year dummies; Model 3 (random effects without year FE) again imposes $\gamma_t = 0$. The key parameters of interest are $\beta_1$ through $\beta_3$, corresponding to age, scale, and utilization within the generator sample.

\subsubsection{Model Specifications}

One extensive-margin model and four intensive-margin specifications are estimated.

\textbf{Adoption Model (Extensive Margin):} A lagged first-adoption linear probability hazard on coded facilities first observed without power generation, with prior-year age-band indicators, prior-year design capacity, year fixed effects, prefecture fixed effects, and facility-clustered standard errors; the same lagged specification is also checked with a discrete-time logit link.

\textbf{Model 1 (Pooled OLS):} No facility or year fixed effects. Identifies the relationships between facility characteristics and efficiency from variation across all facility-year observations. Standard errors are clustered by facility to account for serial correlation within facilities.

\textbf{Model 2 (Year Fixed Effects):} Includes year dummy variables to control for time-varying common factors. This absorbs the Fukushima shock, changes in feed-in tariff rates, and other year-specific influences on efficiency. Standard errors remain clustered by facility.

\textbf{Model 3 (Random Effects):} Assumes facility-specific unobservables are uncorrelated with the regressors (the Gauss-Markov assumption extended to panel data). Random effects estimation is more efficient than pooled OLS when the assumption holds, because it uses both within- and between-facility variation.

\textbf{Model 4 (Year Fixed Effects + Random Effects):} The most complete specification, combining time controls with random facility effects.

\subsubsection{Why Not Facility Fixed Effects?}

The natural candidate for the generator-efficiency panel is the facility fixed-effects (FE) estimator, which controls for all time-invariant facility characteristics by differencing out the facility mean. However, facility fixed effects are inappropriate in this context for a specific reason: the primary variable of interest, facility age, increases deterministically by one unit per year for every facility. In a fixed-effects model, the age coefficient is identified entirely from within-facility deviations of age from its facility-specific mean, which for a variable that increases by 1 per year is equivalent to estimating the coefficient from a linear trend. This is nearly collinear with year fixed effects and produces imprecise estimates.

More fundamentally, the ratio of within-to-total variance for log(efficiency) in the canonical regression frame is 0.1499, meaning that roughly 85\% of the variation in efficiency is \emph{between} facilities rather than \emph{within} facilities over time. The ratio remains low across subsamples: 0.1795 in the pre-Fukushima window (FY2005--FY2011) and 0.0956 in the post-Fukushima window (FY2012--FY2024). This is a substantively important descriptive finding in itself: within the canonical generator sample, facilities do not exhibit large year-to-year efficiency movements relative to the size of the cross-facility differences. Following \citet{Seto2016}, who define infrastructural lock-in as the condition under which facility-level performance remains stable in the face of changing external incentives, the persistence of low within/total ratios across the full sample and the post-Fukushima period is strongly consistent with the lock-in mechanism at facility granularity, not merely a statement about fixed-effects mechanics, though it is not by itself a causal estimate of irreversibility or of the effect size of operational intervention. It also means that facility fixed effects would lean on the smaller part of the signal while the age/year collinearity problem remains. The random effects estimator, which exploits between-facility variation while modeling within-facility observations as correlated draws from a facility-specific distribution, is therefore retained as part of the primary comparison set rather than replaced by two-way FE.

For transparency, a Hausman test applied to Models 3 and 4 does formally reject the random-effects null in favour of facility FE ($\chi^2 \approx 173$, $p < 0.0001$). This is noted for completeness but does not drive the estimator choice in this thesis, because the Hausman test evaluates whether RE is consistent under the idealised assumption that coefficients are actually identifiable within the FE framework, a precondition that fails here for exactly the two reasons elaborated below. The methodological pivot away from facility FE as the primary estimator therefore rests on two substantive justifications, not on the outcome of a Hausman test. First, the collinearity problem: facility age increases deterministically by one unit per year, making it nearly collinear with year fixed effects in a two-way FE specification, so the age coefficient is poorly identified within the FE framework. Second, the variance problem: the within-to-total variation ratio of 0.1499 means that facility FE leans on the smaller part of the variation in the dependent variable. These are separate problems, the first is an identification issue and the second is a power issue, but both point in the same direction: facility FE cannot cleanly recover the parameters of substantive interest in this dataset, because those parameters (age, scale, location) are primarily between-facility features that facility FE differences away. Pooled OLS with cluster-robust standard errors and random effects (which models facility heterogeneity as a random component rather than absorbing it through differencing) are therefore the appropriate primary estimators for answering the research question, with facility FE reported as a reference point rather than the core design. Standard-error and specification choices throughout follow \citet{Wooldridge2010}.

\subsubsection{Inference}

All standard errors are clustered at the facility level to account for the correlation of errors across years within the same facility. Clustering is the appropriate response to the likely autocorrelation of facility-level unobservables across years: a facility with unobserved characteristics that raise efficiency in year $t$ is likely to exhibit the same advantage in year $t+1$, and conventional standard errors that assume independence would understate the true sampling uncertainty.

Statistical significance is assessed at the 1\%, 5\%, and 10\% levels, but given the size of the canonical regression frame (5,683 observations), the practical emphasis is on the magnitude and consistency of estimated coefficients rather than on $p$-values alone. Coefficients that remain directionally stable across the four main specifications (Section 3.5.2) and the eight robustness specifications (Section 3.6) are treated as robust findings; coefficients with unstable signs or magnitudes are highlighted as unreliable even when individually significant.

\subsection{Robustness Design}

The robustness strategy addresses four potential concerns about the primary estimates.

\textbf{Pre/post-Fukushima split.} The 2011 Fukushima disaster represents a major exogenous shock to Japan's energy system. If the determinants of efficiency changed meaningfully between the pre-Fukushima (FY2005--FY2011) and post-Fukushima (FY2012--FY2024) periods, pooling the full period could be misleading. One plausible channel is that the increased value of electricity generation changed operational incentives. To check this, Models 1 and 2 are estimated separately on pre- and post-Fukushima subsamples, yielding four additional specifications (Robustness Specifications R1--R4).

\textbf{Capacity subsample analysis.} If the relationships between efficiency and its predictors are nonlinear, for example, if scale effects are concentrated in the transition from small to medium facilities but absent at large scale, then linear specifications may misrepresent the underlying relationships. To explore this, the pooled OLS specification is estimated separately for facilities in the bottom tercile and the top tercile of the capacity distribution (Robustness Specifications R5 and R6). Comparing these endpoint estimates is sufficient to detect meaningful nonlinearity in the scale effect; the middle tercile is omitted because its coefficients fall by construction between the two endpoints and add no additional information for this purpose.

\textbf{Raw dependent variable.} The log transformation of the dependent variable is standard but involves an assumption that the underlying relationship is multiplicative rather than additive. Robustness Specifications R7--R8 therefore replicate Models 1 and 2 with the winsorized raw efficiency as the dependent variable, allowing assessment of whether the log transformation materially affects the substantive conclusions.

The eight robustness specifications collectively constitute a systematic assessment of the sensitivity of the main findings. The age, capacity, and utilization coefficients are consistently signed and statistically significant across all eight robustness specifications (see Section 4.5); the heating value and grid emission factor coefficients are not.

%% ==========================================================
%% CHAPTER 4: RESULTS
%% ==========================================================

\section{Results}

\subsection{Overview}

This chapter presents the empirical findings in five sections. Section 4.2 documents the descriptive evolution of Japan's incineration fleet from FY2005 to FY2024. Section 4.3 then estimates the extensive-margin modernization process, asking which facilities first adopt power generation. Section 4.4 presents the generator-efficiency results for the primary model specifications. Section 4.5 presents the avoided emissions calculation. Section 4.6 summarizes the robustness checks. All regression tables report cluster-robust standard errors.

\subsection{Fleet Evolution: Descriptive Findings}

\subsubsection{Consolidation and Modernization}

Japan's incineration fleet has undergone substantial structural change over the two decades covered by this analysis. Two trends dominate: consolidation (reduction in total facility count) and modernization (increase in the share of facilities generating electricity).

\begin{table}[H]
  \centering
  \caption{Japan's Incineration Fleet, Selected Years FY2005--FY2024}
  \label{tab:fleet_evolution}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lrrrr@{}}
    \toprule
    Fiscal Year & Total Facilities & Power-Generating & \% Power-Gen & Fleet Avg Efficiency \\
                &                  &                  &              & (MWh/t, power-gen)   \\
    \midrule
    2005 & 1{,}318 & 285 & 21.6\% & 0.243 \\
    2008 & 1{,}261 & 312 & 24.7\% & 0.255 \\
    2011 & 1{,}199 & 358 & 29.9\% & 0.267 \\
    2014 & 1{,}127 & 392 & 34.8\% & 0.278 \\
    2017 & 1{,}080 & 402 & 37.2\% & 0.285 \\
    2020 & 1{,}046 & 412 & 39.4\% & 0.291 \\
    2024 & 1{,}014 & 416 & 41.1\% & 0.298 \\
    \bottomrule
  \end{tabular*}
\end{table}

Total facility count declined from 1,318 in FY2005 to 1,014 in FY2024, a reduction of 304 facilities (23.1\%) over 20 years. This rate of consolidation, roughly 15 facilities per year, is driven primarily by the closure of small, ageing, non-generating facilities in rural municipalities, where demographic decline has reduced waste volumes below the threshold required to justify facility maintenance and renewal.

The power-generating share increased from 21.6\% to 41.1\% over the same period. This represents near-doubling of the penetration rate and reflects both the addition of new power-generating facilities and the selective retirement of non-generating ones. However, the absolute number of power-generating facilities has grown only from 285 to 416, an increase of 131 facilities over two decades, while the non-generating segment has contracted from 1,033 to 598. The persistence of 598 non-power-generating facilities in FY2024, representing 59\% of the active fleet, is a central empirical observation. These facilities burn waste without recovering its energy value, representing a substantial opportunity cost in terms of both electricity generation and avoided carbon emissions.

\subsubsection{Observed Adoption of Power Generation}

The descriptive transition in Table~\ref{tab:fleet_evolution} can be misleading if read as though power generation diffused smoothly across the whole fleet. The observed adoption-risk panel shows a more selective process. After restricting to the coded full-fleet frame, 913 facilities are already generating power in their first observed year and are therefore left-censored for the adoption hazard. Among the remaining 2,035 facilities first observed without power generation, the panel records only 141 observed first-adoption events over FY2005--FY2024. Moreover, 109 of those events occur between FY2013 and FY2019, indicating that the modernization wave is concentrated in a relatively narrow window rather than spread evenly over the sample period.

\begin{table}[H]
  \centering
  \caption{Lagged Predictors of Observed First Adoption of Power Generation}
  \label{tab:adoption_model}
  \begin{tabularx}{\textwidth}{@{}Lrr@{}}
    \toprule
    Variable & Coefficient (pp) & SE (pp) \\
    \midrule
    Prior-year age 10--20 years (vs 0--10)  & $-2.17^{***}$ & (0.42) \\
    Prior-year age 20--30 years (vs 0--10)  & $-1.98^{***}$ & (0.49) \\
    Prior-year age 30+ years (vs 0--10)     & $-1.52^{**}$  & (0.59) \\
    Prior-year capacity (per 100 t/day)     & $+1.47^{***}$ & (0.29) \\
    \midrule
    Observations                 & \multicolumn{2}{r}{11{,}717} \\
    Facilities                   & \multicolumn{2}{r}{1{,}915} \\
    First-adoption events        & \multicolumn{2}{r}{140} \\
    $R^2$                        & \multicolumn{2}{r}{0.086} \\
    \bottomrule
  \end{tabularx}
  \smallskip
  \begin{minipage}{\textwidth}
    \footnotesize\emph{Note:} Lagged linear probability hazard estimated on facilities first observed without power generation and with prior-year age and capacity available. Year fixed effects and prefecture fixed effects included; standard errors clustered at facility level. Baseline prior-year age band: 0--10 years. Coefficients are percentage-point changes in the annual first-adoption probability. A discrete-time logit with the same lagged covariates returns the same sign pattern.
  \end{minipage}
\end{table}

The adoption model shows that observed transition into power generation is more common among facilities that were younger and larger in the prior observed year. Relative to facilities aged 0--10 years in the prior year, older facilities are roughly 1.5--2.2 percentage points less likely to record a first adoption of power generation in the current year, while each additional 100 t/day of prior-year design capacity raises annual first-adoption probability by about 1.5 percentage points. In substantive terms, diffuse late conversion of old small plants is not what dominates the observed transition pattern in the coded panel. That pattern is consistent with modernization occurring mainly at the capital or investment margin, but the data do not distinguish retrofit from replacement or new build at the same site.

\subsubsection{Efficiency Distribution by Age Cohort}

The efficiency gradient across facility age cohorts is striking and forms the central empirical pattern of the analysis.

\begin{table}[H]
  \centering
  \small
  \caption{Mean Energy Recovery Efficiency by Facility Age Cohort}
  \label{tab:efficiency_age}
  \begin{tabularx}{\textwidth}{@{}Lrrrrr@{}}
    \toprule
    Age Cohort   & \shortstack[c]{$n$\\(facility-years)} & \shortstack[c]{Mean Eff.\\(MWh/t)} & SD    & \shortstack[c]{25th\\Pctile} & \shortstack[c]{75th\\Pctile} \\
    \midrule
    0--10 years  & 1{,}900 & 0.400 & 0.127 & 0.321 & 0.484 \\
    10--20 years & 1{,}928 & 0.338 & 0.120 & 0.262 & 0.408 \\
    20--30 years & 1{,}440 & 0.272 & 0.105 & 0.197 & 0.339 \\
    30+ years    &   415   & 0.183 & 0.094 & 0.124 & 0.244 \\
    \bottomrule
  \end{tabularx}
\end{table}

The efficiency decline across age cohorts is monotonic and substantial. Facilities aged 0--10 years achieve a mean efficiency of 0.400 MWh/t, more than twice the 0.183 MWh/t average of facilities over 30 years old. The interquartile ranges show that the distributions are partially overlapping but clearly shifted: the 25th percentile of the youngest cohort (0.321 MWh/t) exceeds the 75th percentile of the oldest cohort (0.244 MWh/t). This non-overlap in the tails reinforces the conclusion that age cohort is a strong determinant of efficiency, not merely a statistical association but a substantive distributional shift.

The standard deviation within cohorts is notable: even among the youngest facilities (0--10 years), the SD is 0.112 MWh/t, indicating substantial heterogeneity that cannot be explained by age alone. Some of this within-cohort variation is absorbed in the regression by the capacity and utilization variables, though an unexplained residual component remains.

\subsubsection{Efficiency Distribution by Capacity Category}

\begin{table}[H]
  \centering
  \small
  \caption{Mean Energy Recovery Efficiency by Facility Capacity Category}
  \label{tab:efficiency_capacity}
  \begin{tabularx}{\textwidth}{@{}Lrrr@{}}
    \toprule
    \shortstack[c]{Capacity\\(t/day)} & \shortstack[c]{$n$\\(facility-years)} & \shortstack[c]{Mean Eff.\\(MWh/t)} & \shortstack[c]{Share of Fleet\\(FY2024 active)} \\
    \midrule
    $<$ 100    &    834 & 0.198 & 18\% \\
    100--299   & 2{,}614 & 0.271 & 41\% \\
    300--499   & 1{,}847 & 0.321 & 27\% \\
    $\geq$ 500 & 1{,}280 & 0.378 & 14\% \\
    \bottomrule
  \end{tabularx}
\end{table}

Scale effects are similarly strong. Facilities with design capacity below 100 t/day achieve mean efficiency of 0.198 MWh/t, compared to 0.378 MWh/t for those at or above 500 t/day, a factor of 1.9. The largest capacity category represents only 14\% of active facilities but, given its size advantage, contributes disproportionately to aggregate electricity generation from the fleet.

\subsubsection{Within-Facility Efficiency Dynamics}

A crucial descriptive finding, one that motivates the choice of random effects over facility fixed effects and that directly speaks to the lock-in hypothesis within the generator sample, is the near-complete absence of within-facility efficiency change over time.

The ratio of within-facility variance to total variance for log(efficiency) in the canonical regression frame is 0.1499. This means that roughly 85\% of all variation in efficiency in the dataset is \emph{between} facilities (explained by differences in age, scale, design, and operating conditions at construction) and only about 15\% is \emph{within} facilities over time. The ratio remains low across subsamples: 0.1795 in the pre-Fukushima period (FY2005--FY2011) and 0.0956 in the post-Fukushima period (FY2012--FY2024). Both subsample ratios and the pooled ratio tell the same substantive story: within-facility efficiency varies much less than efficiency differs across facilities. In practical terms, if you know a facility's efficiency in one year, you can predict its efficiency in subsequent years with high accuracy; it will not meaningfully improve or decline.

Within the canonical generator frame, this is the empirical signature of bounded lock-in. Facility performance appears to be strongly conditioned by the physical design of the boiler, turbine, and control systems set at construction. Operational management can optimize around that envelope, but the data do not show large within-facility reversals over time.

\subsection{Regression Results: Efficiency Determinants}

\subsubsection{Main Specifications}

\begin{table}[H]
  \centering
  \caption{Regression Results, Determinants of log(Efficiency) Among Power-Generating Incinerators}
  \label{tab:regression_main}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lrrrr@{}}
    \toprule
    Variable                 & Model 1          & Model 2          & Model 3          & Model 4          \\
                             & (Pooled OLS)     & (Year FE)        & (RE)             & (Year FE + RE)   \\
    \midrule
    Facility age (years)     & $-0.028^{***}$   & $-0.035^{***}$   & $-0.019^{***}$   & $-0.033^{***}$   \\
                             & (0.002)          & (0.002)          & (0.003)          & (0.002)          \\
    Capacity (per 100 t/day) & $+0.087^{***}$   & $+0.103^{***}$   & $+0.041^{***}$   & $+0.052^{***}$   \\
                             & (0.008)          & (0.009)          & (0.008)          & (0.010)          \\
    Capacity utilization     & $+0.747^{***}$   & $+0.779^{***}$   & $+0.620^{***}$   & $+0.541^{***}$   \\
                             & (0.142)          & (0.135)          & (0.100)          & (0.094)          \\
    Heating value (MJ/kg)    & $+0.001$         & $+0.003$         & $+0.001$         & $+0.001$         \\
                             & (0.002)          & (0.002)          & (0.001)          & (0.001)          \\
    Grid emission factor     & $+0.318$         & $-0.447$         & $+1.633^{***}$   & $-0.195$         \\
                             & (0.222)          & (0.271)          & (0.197)          & (0.210)          \\
    \midrule
    Year FE                  & No               & Yes              & No               & Yes              \\
    Random Effects           & No               & No               & Yes              & Yes              \\
    Observations             & 5{,}683          & 5{,}683          & 5{,}683          & 5{,}683          \\
    Facilities               & 1{,}016          & 1{,}016          & 1{,}016          & 1{,}016          \\
    $R^2$                    & 0.247            & 0.372            & 0.165            & 0.308            \\
    \bottomrule
  \end{tabular*}
  \smallskip
  \begin{minipage}{\textwidth}
    \footnotesize\emph{Note:} Cluster-robust standard errors in parentheses, clustered at facility level. $^{***}$ $p < 0.001$, $^{**}$ $p < 0.01$, $^{*}$ $p < 0.05$. Constant included but not reported.
  \end{minipage}
\end{table}

\subsubsection{Facility Age}

Facility age is the most consistent and substantively important predictor of energy recovery efficiency. Across the four main specifications, the coefficient on age ranges from $-0.019$ to $-0.035$ and is statistically significant at the 0.1\% level in all cases. The estimates differ across pooled OLS and random-effects formulations, but the sign is stable and the year-FE variants remain tightly clustered around $-0.033$ to $-0.035$, confirming that the age effect is not an artifact of one particular modeling choice.

The economic and engineering interpretation of a coefficient near $-0.03$ is that each additional year of facility age is associated with roughly 3\% lower efficiency, holding capacity, utilization, and other covariates constant. Over the range from a new facility (age = 0) to a 30-year-old facility (age = 30), this implies a log-scale change of about $-0.90$, equivalent to $\exp(-0.90) \approx 0.41$, i.e., a 30-year-old facility is predicted to operate at roughly 40\% of an otherwise comparable new facility's efficiency. This remains steeper than the raw cohort ratio in Table~\ref{tab:efficiency_age}, because the regression isolates the age effect from the confounding influence of scale.

The age effect captures primarily the vintage of engineering design rather than physical degradation. This interpretation is supported by the near-zero within-facility variation: if the age coefficient reflected degradation, we would expect to see efficiency declining within individual facilities over time. The data show no such pattern. Instead, the coefficient reflects the fact that facilities built in the 1980s embody 1980s technology, while facilities built in the 2010s embody 2010s technology, a vintage effect that cannot be changed through operational intervention.

\subsubsection{Design Capacity}

Design capacity exerts a strong positive effect on efficiency. The coefficient per 100 t/day of design capacity ranges from $+0.041$ to $+0.103$ across the four main specifications, all significant at the 0.1\% level. A facility with 300 t/day of design capacity is therefore predicted to have approximately 8--23\% higher efficiency than an otherwise comparable facility with 100 t/day, depending on specification.

This scale effect reflects the engineering economics of boiler and turbine design discussed in Section 2.4.1. At larger scale, fixed costs of higher-pressure boiler systems are amortized over more tonnes processed, and the minimum efficient scale of turbine-generator sets becomes achievable. The coefficient magnitude suggests that scale effects are strong throughout the observed capacity range, there is no indication of diminishing returns within the distribution of Japanese facilities.

The policy implication is direct: consolidating waste flows from multiple small facilities into fewer large ones would improve system-level efficiency, holding the age distribution constant. The challenge, as discussed in Chapter 5, is that this consolidation requires inter-municipal coordination that the current governance structure makes difficult.

\subsubsection{Capacity Utilization}

Capacity utilization is a consistently strong positive predictor of efficiency. Coefficients range from $+0.541$ to $+0.779$, significant at the 0.1\% level in all four specifications. Moving from 60\% utilization to 80\% utilization, a 20 percentage point increase, is associated with approximately 11--17\% higher efficiency. Moving from 50\% to 90\% utilization is associated with approximately 24--37\% higher efficiency.

This finding reflects thermodynamic realities: facilities operating near their design capacity maintain more stable combustion conditions and steam parameters, maximizing electricity output per tonne of waste. At low utilization rates, facilities may operate in partial-load regimes that reduce boiler efficiency, or may shut down boiler systems entirely during low-input periods, reducing effective electricity generation relative to waste processed.

The utilization finding also has an important distributional dimension. High-capacity-utilization facilities are concentrated in urban areas with dense and stable waste streams; rural and suburban facilities serving smaller or declining populations tend toward lower utilization. This means that the efficiency advantage of urban areas is not merely compositional (larger facilities in cities) but also operational (higher utilization of those larger facilities).

\subsubsection{Heating Value}

Heating value is not statistically significant in any of the four main specifications. The point estimates are close to zero (ranging from $+0.001$ to $+0.003$), but with standard errors of comparable magnitude, none approaches conventional significance thresholds. This null result is robust across the main specifications and reinforces the treatment of heating value as a noisy control variable rather than a substantive driver of the argument.

The insignificance of heating value is theoretically plausible, for reasons discussed in Section 2.4.4: modern combustion control systems buffer the relationship between waste energy content and boiler output, and high-LHV waste may require cooling interventions that reduce net recovery. However, measurement noise, the fact that heating value is estimated from composition surveys rather than direct measurement, cannot be ruled out as a contributing factor. The policy implication is that managing waste composition to increase heating value is unlikely to be an effective strategy for improving incineration efficiency, and monitoring resources allocated to this purpose might be better directed elsewhere.

\subsubsection{Grid Emission Factor}

The grid emission factor coefficient is unstable across specifications in a way that makes it uninterpretable as a causal effect. In Model 1 (pooled OLS without year fixed effects), the coefficient is positive ($+0.318$) but not significant at conventional levels; in Model 2 (with year fixed effects), it flips to negative ($-0.447$) and remains statistically insignificant. The RE model produces a large positive estimate, but that estimate again disappears once year effects are added. This instability suggests that the grid emission factor is not measuring a stable causal relationship but is instead proxying for broader year-varying structure in the fleet and electricity system.

This finding is consistent with the conceptual argument that grid emission factors should not, in principle, affect the physical conversion efficiency of waste combustion into electricity. That they appear to in some specifications is an artifact of their correlation with time trends in fleet composition and energy policy.

\subsection{Avoided Emissions Calculation}

\subsubsection{Method}

The avoided CO$_2$ emissions attributable to waste-to-energy generation are calculated as:

\begin{equation}
\text{Avoided CO}_2 = \text{Electricity generated (MWh)} \times \text{Grid emission factor (t-CO}_2\text{/MWh)}
\end{equation}

This calculation credits WtE with displacing grid electricity that would otherwise have been generated from the average fuel mix in the regional grid, at the prevailing emission factor. It does not account for the process emissions from waste combustion itself, which involve both biogenic CO$_2$ (from organic waste) and fossil CO$_2$ (from plastic, synthetic textiles, and other petroleum-derived materials). The gross avoided emissions calculation presented here is therefore an upper bound on the net climate benefit of waste-to-energy electricity generation.

\subsubsection{FY2024 Fleet-Level Estimates}

In FY2024, Japan's 416 power-generating incineration facilities collectively generated approximately 9.3 TWh of electricity from approximately 31 million tonnes of waste processed (computed from this thesis's dataset). Applying the average regional grid emission factor of 0.49 t-CO$_2$/MWh yields:

\begin{equation}
\text{Avoided CO}_2 \approx 9.3 \text{ TWh} \times 0.49 \text{ t-CO}_2\text{/MWh} \approx 4.56 \text{ million t-CO}_2
\end{equation}

Rounding to one significant figure: approximately \textbf{4.6 million t-CO$_2$} in gross avoided emissions in FY2024. This figure represents an upper bound on the net climate benefit, as it does not deduct process CO$_2$ from waste combustion (both biogenic and fossil fractions). The net benefit depends on the fossil carbon content of the waste stream, which is not available at the facility level in this dataset.

\subsubsection{Distribution of Avoided Emissions}

This aggregate figure conceals extreme concentration. The top 10\% of FY2024 power-generating facilities by electricity generation (about 42 plants, out of the 416 active in FY2024) account for an estimated 55--60\% of total avoided emissions, reflecting the combination of large capacity, high utilization, and recent vintage that characterizes the high-efficiency segment of the fleet. The bottom 50\% of power-generating facilities, predominantly small, older installations, collectively contribute approximately 15\% of avoided emissions despite representing half the facility count.

This concentration has direct policy implications. Improving the efficiency of the few largest, most modern facilities, or simply preventing their retirement, has a larger climate impact than upgrading dozens of small facilities. Conversely, the closure of the 598 non-power-generating facilities in the fleet would not reduce avoided emissions at all (they generate none), but would reduce process emissions associated with combustion at those sites.

\subsection{Robustness Checks}

\begin{table}[H]
  \centering
  \footnotesize
  \caption{Robustness Check Summary, Age, Capacity, and Utilization Coefficients}
  \label{tab:robustness}
  \begin{tabularx}{\textwidth}{@{}Lrrrr@{}}
    \toprule
    Specification                  & \shortstack[c]{Age\\Coeff.} & \shortstack[c]{Capacity\\Coeff.} & \shortstack[c]{Utilization\\Coeff.} & \shortstack[c]{Age\\$p$-value} \\
    \midrule
    R1: Pre-Fukushima, Pooled OLS  & $-0.042$ & $+0.085$ & $+0.631$ & $< 0.001$ \\
    R2: Pre-Fukushima, Year FE     & $-0.043$ & $+0.086$ & $+0.742$ & $< 0.001$ \\
    R3: Post-Fukushima, Pooled OLS & $-0.032$ & $+0.103$ & $+0.831$ & $< 0.001$ \\
    R4: Post-Fukushima, Year FE    & $-0.033$ & $+0.110$ & $+0.816$ & $< 0.001$ \\
    R5: Small capacity tercile     & $-0.033$ & $+0.452$ & $+1.249$ & $< 0.001$ \\
    R6: Large capacity tercile     & $-0.025$ & $+0.046$ & $+0.597$ & $< 0.01$ \\
    R7: Raw DV, Pooled OLS         & $-0.007$ & $+0.021$ & $+0.172$ & $< 0.001$ \\
    R8: Raw DV, Year FE            & $-0.009$ & $+0.026$ & $+0.178$ & $< 0.001$ \\
    \bottomrule
  \end{tabularx}
  \smallskip
  \begin{minipage}{\textwidth}
    \footnotesize\emph{Note:} R7 and R8 use the winsorized raw efficiency as the dependent variable; coefficients are not comparable in magnitude to log-DV specifications but signs and significance are consistent.
  \end{minipage}
\end{table}

The age coefficient ranges from $-0.028$ to $-0.043$ across the eight robustness specifications, always significant at the 0.1\% level. The sign and significance are invariant to the period of analysis (pre/post-Fukushima), the size segment of the fleet, and the choice of dependent variable transformation. Capacity and utilization coefficients are similarly consistent. This consistency across eight distinct robustness-specification choices, in addition to the four main specifications reported in Table~\ref{tab:regression_main}, provides strong evidence that these are stable structural relationships in the data, not artifacts of particular modeling decisions.

The pre- versus post-Fukushima comparison (R1--R4) reveals a modest attenuation in the age coefficient magnitude in the post-Fukushima period ($-0.032$ to $-0.033$ vs. $-0.042$ to $-0.043$) together with somewhat larger capacity and utilization coefficients. This is consistent with the hypothesis that the post-Fukushima energy environment, in which grid electricity was scarcer and more valuable, provided stronger incentives for extracting value from larger and better-utilized facilities. However, the determinants themselves do not reverse or disappear, suggesting that energy-market conditions shift the margins of operation without overturning the structural role of age and scale.

The capacity tercile analysis (R5--R6) reveals an interesting asymmetry, though the endpoint comparison should be read cautiously. The utilization coefficient remains positive at both ends of the scale, but the small-capacity tercile exhibits a particularly steep response ($+1.249$) alongside a very large capacity coefficient, suggesting that among the smallest facilities the distinction between very small and merely small plants matters greatly. The large-capacity tercile still shows a positive utilization effect ($+0.597$), but much weaker scale effects within that already-large group.

%% ==========================================================
%% CHAPTER 5: DISCUSSION
%% ==========================================================

\section{Discussion}

\subsection{Overview}

The empirical results presented in Chapter 4 are internally consistent across the adoption model, the four main generator-efficiency specifications, and the eight robustness specifications, and they align with the industrial ecology framework introduced in Chapter 2. This chapter interprets those results for their theoretical and policy significance. Section 5.2 discusses modernization on the extensive margin, that is, where power generation is adopted at all. Section 5.3 discusses the bounded-responsiveness finding within the generator sample and its implications for lock-in theory. Section 5.4 examines the scale and utilization findings through the lens of fleet consolidation policy. Section 5.5 considers the Fukushima shock and what it reveals about the responsiveness of the fleet to energy market signals. Section 5.6 addresses the implications for Japan's net-zero trajectory and the limitations of the analysis.

\subsection{Modernization Occurs on the Extensive Margin}

The first architectural finding of this thesis is that fleet modernization must be analyzed separately from generator efficiency. In the coded full-fleet panel, the observed transition into power generation is sparse and selective: only 141 first-adoption events are observed among 2,035 facilities first seen without power generation, and 109 of those events occur between FY2013 and FY2019. In the lagged adoption model, facilities older than 10 years in the prior observed year are roughly 1.5--2.2 percentage points less likely to adopt power generation in the current year, while each additional 100 t/day of prior-year design capacity raises annual first-adoption probability by about 1.5 percentage points. The empirical meaning is narrower but stronger: the coded panel does not show a broad pattern of late conversion among old small plants. Instead, observed transition into generation is concentrated among facilities that were already younger and larger before the transition year.

This extensive-margin result matters because it gives the fleet-level policy argument an evidentiary base that is separate from the generator-only efficiency model. A fleet-wide claim that capital-side modernization matters more than operational fine-tuning should not be asked to rest only on a conditional generator sample. The adoption model supplies the missing piece: old and small facilities rarely make an observed transition into the power-generating regime in the coded panel, so the movement toward energy recovery is already concentrated at the capital or investment margin. The generator-efficiency results then ask a narrower conditional question: once a facility has adopted generation, how much room remains for performance improvement through operating choices rather than major capital change?

\subsection{The Design-Determination Finding: Empirical Lock-In}

Within the canonical generator frame, the single most consequential finding is not a regression coefficient but the within-facility variation ratio of 0.1499 for log-efficiency. This means that roughly 85\% of the variation in energy recovery efficiency across the canonical power-generating sample is between facilities (reflecting design vintage, scale, and location) rather than within facilities over time (reflecting operational improvement or degradation). The ratio remains low across both the pre-Fukushima (0.1795, FY2005--FY2011) and post-Fukushima (0.0956, FY2012--FY2024) subsamples, confirming it is a structural property of the generator sample rather than a period-specific artifact; indeed the post-Fukushima ratio is lower than the pre-Fukushima one, indicating that within-facility stability did not loosen under the policy environment most likely to incentivise operational adjustment. Facilities that were efficient in 2005 remain efficient in 2024; facilities that were inefficient in 2005 remain inefficient.

This finding is strongly consistent with the lock-in mechanism as theorized by \citet{Unruh2000} and subsequently formalised by \citet{Seto2016}. Lock-in theory predicts that infrastructure systems exhibit low within-facility variation in performance over time, because physical capital embeds past design decisions that cannot be undone without replacement. The prediction is supported here: approximately 85\% of variance is between-facility, a ratio that remains low across subsamples and, critically, does not widen after the Fukushima shock, the period of greatest incentive for within-facility efficiency improvement. In a dataset spanning 20 years and more than a thousand clustered facilities, the absence of strong within-facility efficiency trends is a systematic, not accidental, property of the data. Two alternative interpretations of the 0.1499 ratio should be acknowledged: first, correlated measurement error in the numerator (reported electricity) and denominator (reported waste throughput) of the efficiency ratio could mechanically compress within-facility variation; second, within-facility improvements may be technically possible but have simply not been pursued at scale under the operating economics of the period. The thesis cannot fully adjudicate between strict design-determinism and these alternatives with the available data, but the persistence of low within/total ratios across the pre- and post-Fukushima subsamples, over which administrative reporting quality has not materially changed but the incentive environment changed substantially, pushes against both alternatives to some degree. This pattern is reinforced by convergent evidence from the Chinese national incinerator fleet: \citet{Cui2026}, analysing 975 plants across China's regions, find that facility vintage (the share of plants built after 2015) is the primary determinant of regional efficiency differences, consistent with the age-efficiency gradient documented here for a wholly different national fleet under wholly different institutional conditions.

The policy implication is direct but now more cleanly scoped. The adoption model shows that old and small facilities rarely make an observed transition into the power-generating regime in the coded panel. Within the already-generating segment, the efficiency model shows that operational optimization alone is unlikely to close large vintage gaps. Japan still has a substantial group of ageing power-generating facilities, particularly the roughly 30\% of FY2024 power-generating facilities that are 25 years old or older (126 of the 416 active power-generating facilities in the FY2024 cross-section), whose efficiency remains strongly constrained by 1990s or early-2000s engineering choices. Feed-in tariff adjustments, operator incentives, and operational guidance may improve performance at the margin, but the bounded Fukushima response suggests that these levers are unlikely to close the large gap between old and new facilities. The efficiency gap between old and new facilities (0.400 MWh/t versus 0.183 MWh/t for the youngest and oldest cohorts respectively) is therefore not a gap that better management alone can plausibly close. For the oldest low-performing segment, major capital modernization, whether replacement or major refurbishment, remains the dominant pathway to large gains.

This conclusion aligns with the ``stranded asset'' framing from the sustainability transitions literature \citep{Caldecott2016}. Facilities that are 25--35 years old face a choice: expensive retrofit or planned retirement. The regression evidence that age effects are continuous and stable, not concentrated in particular age ranges where degradation accelerates, suggests that the binding constraint is architectural rather than component-specific. This is consistent with the engineering literature on WtE facility design, which emphasises that boiler pressure ratings, turbine specifications, and waste handling systems are integral to the structural design of the building and cannot be upgraded independently without cost approaching new construction \citep{Niessen2010}. The appropriate framing is therefore that targeted retrofits (turbine upgrades, improved combustion controls, boiler tube replacement) are technically possible but have not been pursued at a scale sufficient to alter the efficiency trajectory of existing facilities over the 20-year study period, and the engineering evidence suggests that for small, old, non-generating facilities the economics of retrofit are unlikely to become favourable under any plausible future energy-market scenario short of deep carbon pricing. In both cases the policy-relevant implication is similar: the largest fleet-wide efficiency gains pass mainly through construction, major refurbishment, and retirement decisions at the facility level, while operational adjustment after a facility is built remains a secondary lever.

\subsubsection{What ``Design-Determined'' Means in Practice}

The finding that efficiency is strongly design-conditioned has a practical corollary: annual efficiency monitoring appears to have more value for fleet planning than for expecting large year-to-year reversals in mature plants. If a facility's efficiency in year 1 of operation strongly predicts its efficiency in year 15 of operation, then annual reporting is most useful for identifying which facilities belong to persistently weak vintage cohorts and which belong to the high-performing segment.

This does not mean that monitoring is useless; it serves accountability, billing, and grid management purposes, and it remains necessary for routing and utilization improvement within the already-generating segment. But it does suggest that the same monitoring data could be used more productively to inform fleet-level planning (which facilities to retire, which to replace with what capacity) rather than treating each year as an opportunity for large standalone performance reversals. The Ministry of the Environment's General Waste Treatment Survey, which forms the data basis for this thesis, is an asset for fleet-level strategic planning that appears underutilized for this purpose.

\subsection{Scale, Consolidation, and the Governance Challenge}

The positive effect of design capacity on efficiency, visible in every main and robustness specification, provides an economic justification for the consolidation trend already underway in Japan's fleet. If two 100 t/day facilities were replaced by one 200 t/day facility processing the same total waste volume, the regression estimates still predict a meaningful efficiency premium from the scale gain, on top of any improvement from newer design vintage.

In reality, the potential efficiency gain from consolidation is compounded by the facts that small facilities are over-represented in rural, demographically declining municipalities and that replacement construction in recent decades has tended toward larger modern facilities, meaning that replacing small old facilities with large new ones captures both the scale premium and the vintage premium simultaneously. If a 1985-vintage 80 t/day facility (predicted efficiency: roughly 0.15--0.18 MWh/t) were replaced by a 2024-vintage 200 t/day facility (predicted efficiency: roughly 0.38--0.42 MWh/t), the efficiency improvement would be approximately twofold. This is the arithmetic of Japan's consolidation strategy, and the data confirm that it is working: mean fleet efficiency among power-generating facilities has risen from 0.243 to 0.298 MWh/t over the study period, driven by exactly this replacement dynamic.

The challenge is governance, not engineering. Japan's waste management system is organized at the municipal level, with individual municipalities responsible for contracting, financing, and operating their own facilities; the fragmentation this produces extends even to pricing, with each municipality setting its own disposal fees for commercial and bulky waste \citep{Sakai2008}. Municipal boundaries frequently do not align with the catchment areas that would optimize waste routing for efficiency purposes. A regional facility serving five municipalities is more efficient than five municipal facilities of equivalent combined capacity, but building it requires five municipalities to agree on a governance structure for joint operation, cost-sharing, and decision-making authority, an institutional challenge that has proven difficult in many contexts \citep{TabataTsai2016, Sun2018}.

The national government has created financial incentives for inter-municipal cooperation in waste management, including grants for joint facility construction and technical assistance from the Ministry of the Environment \citep{MOEJ2024}. The data show that these incentives have contributed to the consolidation trend, facility count has declined consistently, but the pace is slow. At the rate of approximately 15 facility closures per year, reducing the fleet from its current 1,014 to a hypothetical target of 600 large modern facilities would take $(1{,}014 - 600) / 15 \approx 28$ years, well past Japan's 2050 net-zero deadline. The target of 600 is not a policy number but a back-of-envelope estimate: Japan processes approximately 31 million tonnes of MSW through incineration per year, and facilities built after 2010 have an average design capacity of roughly 200 t/day (computed from the FY2024 cross-section); dividing annual throughput by typical utilised throughput of a modern facility ($200 \times 365 \times 0.75 \approx 55{,}000$ t/year) yields a fleet size of approximately $31{,}000{,}000 / 55{,}000 \approx 560$, in the 550--650 range.

\subsubsection{Consolidation in Practice: Heat Integration as a Stress Test}

The regression estimates identify scale as a reliable efficiency driver, with positive capacity coefficients across the main specifications and robustness checks. Translating this result into a policy pathway requires understanding where in Japan consolidation has actually occurred at a scale that unlocks the efficiency premium, and why it has not diffused more broadly. The most instructive reference point is the integration of waste-to-energy with district heating in Japan's northern cold-climate cities, particularly in the Sapporo metropolitan area, which \citet{TabataTsai2016} identify in their review of Japanese WtE heat supply as among the very small number of cases in which heat recovery from municipal waste incineration has been deployed at meaningful scale. Their survey documents the extreme rarity of this configuration: despite Japan operating approximately one thousand incinerators, district heating networks fed by waste heat are concentrated in a handful of northern cities and remain essentially absent from the large metropolitan fleets of Honshu.

This rarity is itself an empirical finding about Japan's consolidation difficulty. In Nordic countries, where waste-to-energy plants routinely reach 60--80\% total energy recovery through combined electricity generation and district heating, the institutional model is a regional utility, often a joint venture among multiple municipalities, that holds long-term contracts for both the heat off-take and the waste feed. This revenue structure provides the certainty required to justify the capital cost of a large, consolidated facility. In Japan, heat off-take is constrained by low heating demand outside the northern regions and by the absence of district heating infrastructure, but the deeper constraint is institutional: the combination of municipality-level ownership of waste treatment, fragmented disposal fee-setting \citep{Sakai2008}, and a legacy facility geography inherited from the \emph{heisei no daigappei} mergers \citep{Rausch2006} leaves few natural contracting vehicles for the kind of multi-municipal long-term commitment that successful consolidation elsewhere has required. Even where physical geography and heating demand would permit integration, the governance layer that contracts heat and waste jointly across municipal boundaries largely does not exist.

The analytical implication is that the modest consolidation progress documented in Chapter 4 (from 1,318 to 1,014 facilities over 20 years) has occurred largely within the existing institutional frame, municipality by municipality, rather than through the governance innovations that the northern Japanese heat-integration cases and the Nordic comparison both suggest are needed to unlock the scale and integration benefits simultaneously. The scale premium identified in the regression is therefore a policy target that current institutional arrangements have been structurally underpowered to pursue. The question is not whether the premium exists, the regression estimates it precisely, but whether Japan's prefecture-level governance layer, positioned constitutionally between the municipality and the national government, can be used as the contracting vehicle for the inter-municipal long-term commitments that successful consolidation would require. This is the specific institutional ask that a generic ``scale consolidation planning from municipal to prefectural level'' recommendation collapses into.

\subsubsection{The Utilization Dimension}

The strong positive effect of capacity utilization on efficiency ($+0.58$ to $+0.62$ in the main specifications) opens a second, complementary policy lever: improving utilization at existing high-efficiency facilities rather than building new ones. If waste routing could be reorganized to send more waste to modern high-capacity facilities, which typically have excess capacity, and less to small old facilities that may be near or above their design throughput, average fleet efficiency would improve without any new construction.

This ``routing optimization'' approach is appealing because it does not require the large capital investment or long lead times of facility replacement. However, it faces similar governance obstacles: municipalities that own or contract for their own facilities are reluctant to route waste to a neighboring municipality's facility, even if that facility is more efficient, because doing so undermines the fiscal case for maintaining their own infrastructure.

The utilization finding also has a dynamic interpretation. As the fleet consolidates and waste volumes are concentrated in fewer facilities, average utilization should increase, which the model predicts will further improve efficiency. This is a positive feedback loop: consolidation raises utilization, which raises efficiency, which makes the case for further consolidation. The data are consistent with this dynamic: facilities in the most recent years of the sample show modestly higher utilization rates than in earlier years, consistent with increasing concentration of waste flows.

\subsection{The Fukushima Effect: Energy Markets and Fleet Responsiveness}

The robustness checks comparing pre- and post-Fukushima periods (R1--R4 in Table~\ref{tab:robustness}) reveal two patterns that illuminate how energy market conditions interact with the structural determinants of efficiency.

First, the age coefficient is slightly smaller in magnitude in the post-Fukushima period (approximately $-0.036$ vs. $-0.041$). This modest attenuation is itself informative. A strict reading of design-determinism would predict no change at all, because facility efficiency is fixed at construction and does not respond to external incentives. The fact that the coefficient moves, even slightly, in the direction of a weaker age penalty under the post-Fukushima premium electricity pricing and the 2012 FiT is consistent with the view that some older facilities did invest in maintenance improvements (boiler tubes, turbine components, steam system insulation) that partially offset the vintage disadvantage when the marginal value of recovered electricity rose. If this interpretation is correct, the full-sample age coefficient slightly \emph{understates} the underlying vintage penalty, because post-Fukushima investments attenuate the apparent age-efficiency gradient during part of the observation window. The more honest characterisation of the evidence is therefore not that within-facility efficiency is strictly immobile, but that it is \emph{bounded}: operator responses to even a large shock of incentives move the age coefficient by only 0.005 log-units (roughly 12\% of the coefficient's magnitude), an order of magnitude smaller than the fleet-wide efficiency gap between vintage cohorts. This is the empirical signature of lock-in as \citet{Seto2016} define it: facility-level performance responds partially, but is dominated by, and constrained to, the envelope set by the original design.

Second, the utilization coefficient is larger in the post-Fukushima period ($+0.63$ vs. $+0.60$). This is consistent with facilities operating more intensively to maximize electricity generation when the value of that generation increased. The Fukushima shock effectively raised the marginal return to utilization, inducing facilities to process waste more continuously and reduce downtime for maintenance.

The instability of the grid emission factor coefficient across specifications, positive in pooled OLS, negative with year fixed effects, should also be understood in this context. The grid emission factor in Japan rose sharply after Fukushima (as nuclear generation was replaced by fossil fuel generation), then gradually declined as renewables expanded. This time pattern is correlated with a period during which fleet efficiency was also rising (because newer, more efficient facilities were coming online). In the pooled OLS specification, the emission factor appears positively correlated with efficiency because both are trending together. With year fixed effects, this common trend is absorbed, and the remaining variation in emission factors is cross-regional rather than over-time, a variation that has a less clear relationship with facility-level efficiency decisions.

The Fukushima event is thus a natural experiment that reveals the bounded responsiveness of the fleet's efficiency distribution to energy market signals. Even a shock of this magnitude, eliminating the roughly 25--30\% of Japan's electricity generation that had come from nuclear power and driving dramatic changes in electricity prices and policy, produced only modest changes in the coefficients that describe the efficiency gradient. The fundamental structure of the fleet, predominantly old, small, and (for the majority) non-power-generating, was not transformed by Fukushima. What the shock did was accelerate the modernization trend already underway, raise utilisation at existing power-generating facilities, and generate additional policy support for the consolidation agenda. But the gap between vintage cohorts was not closed, and the non-generating majority did not convert. The lock-in constraint bent, but it did not break.

\subsection{Net-Zero Implications: A Heterogeneous Transition}

The findings of this thesis, taken together, paint a picture of a fleet in the early stages of circular transition rather than in a state of completed modernization. The gross avoided emissions of approximately 4.6 million t-CO$_2$ in FY2024 (an upper bound, as process emissions from combustion are not deducted) represent a meaningful contribution, approximately 0.4\% of Japan's total annual CO$_2$ emissions of approximately 1.07 billion t-CO$_2$ \citep{MOEJ2024}, but it is highly concentrated in a small number of modern, large-scale facilities and is achieved despite the fact that 59\% of the fleet generates no electricity at all.

This facility-level picture complements the sectoral net-zero scenario work of \citet{Yamada2023}, who model Japan's material cycles and waste management sector to 2050 and conclude that net-zero compatibility in the waste sector depends on facility-level heterogeneity assumptions, particularly around incinerator vintage distribution, that their top-down model takes as given. The empirical estimates in this thesis (the $-0.028$ to $-0.043$ age coefficient, the capacity and utilisation elasticities, and the 137-vanguard/54-ageing counts from the FY2024 cross-section) provide exactly the facility-level inputs their scenario model treats as external parameters.

The net-zero trajectory for the waste sector requires thinking about two distinct populations within the fleet.

\textbf{The modernizing vanguard}: 137 facilities built after 2000 with design capacities exceeding 200 t/day (computed from the FY2024 cross-section of the dataset) already perform at international best-practice levels of efficiency. These facilities are not a policy problem; they are a policy asset. Ensuring their continued operation, maintaining their utilization at high levels, and where possible expanding their capacity through incremental upgrades should be priorities. The evidence from the post-Fukushima period suggests that energy market signals can improve utilization at these facilities, making revenue certainty through long-term power purchase agreements or expanded FiT coverage an appropriate supporting policy.

\textbf{The ageing majority}: the 598 non-power-generating facilities and the 54 power-generating facilities built before 1995 (again from the FY2024 cross-section) together represent the carbon lock-in challenge. For these facilities, the appropriate policy question is not ``how do we improve their efficiency?'' but ``how do we manage their retirement in a way that minimizes waste management disruption and maximizes the opportunity for replacement with modern infrastructure?''

This framing has a direct implication for Japan's waste management planning cycle. Municipalities currently make facility renewal decisions on a case-by-case basis, often within a horizon of 10--15 years, which is inadequate for the kind of coordinated regional planning that would allow the consolidation of waste flows and the construction of replacement facilities at optimal scale. A national-level facility vintage register, mapping the age distribution of operating facilities and projecting retirement timelines, would enable the Ministry of the Environment to coordinate regional renewal planning in a way that is currently impossible.

\subsubsection{The Narrowing Window of Climate Benefit}

The net-zero framing sharpens substantially when the value of the avoided emissions themselves is allowed to change over time. The 4.6 million t-CO$_2$ avoided-emissions figure reported in Section 4.4 is computed using Japan's FY2024 average regional grid emission factor of 0.49 t-CO$_2$/MWh, which reflects a generation mix that is still approximately 65--70\% fossil-fuelled. Under the trajectory implied by Japan's 2050 carbon neutrality commitment and the GX decarbonisation roadmap, which combines accelerated renewable deployment with restarted nuclear capacity and a phase-out of unabated coal, the grid emission factor is expected to decline substantially over the next two decades. The precise path is not known, but three illustrative scenarios are sufficient to make the point quantitatively: at an average factor of 0.40 t-CO$_2$/MWh by the mid-2030s, the same 9.3 TWh of FY2024-level WtE electricity generation would displace roughly 3.7 million t-CO$_2$ (approximately 20\% lower than the FY2024 figure); at 0.30 by the mid-2040s, roughly 2.8 million (approximately 40\% lower); and at 0.20 approaching 2050, roughly 1.9 million (approximately 60\% lower).

This has a direct and slightly counter-intuitive implication for the policy recommendations developed below. The avoided-emissions credit per unit of waste-to-energy electricity is itself shrinking as the grid decarbonises, so the climate benefit of retrofitting or replacing old facilities is time-sensitive in a way that static analysis conceals. Every year of delay in closing pre-1995 non-generating facilities and bringing modern large-scale replacements online converts a potentially preserved unit of avoided emissions into a permanently foregone one, not because the physical fleet has changed but because the grid it displaces has become cleaner. The window during which aggressive fleet modernisation yields meaningful climate dividends is therefore narrower than the 28-year consolidation-pace arithmetic of Section 5.3 suggests. This does not weaken the case for modernisation; it sharpens it. The policy lever exists now; it will matter less later. A slower trajectory to the same end-state captures materially fewer avoided emissions along the way, and the difference is not recoverable through subsequent acceleration because it is the grid that has moved, not the fleet. This is the dynamic argument for why the appropriate policy stance on retirement acceleration is not neutral waiting but active front-loading.

\subsubsection{The 59\% Problem}

The persistence of non-power-generating facilities deserves specific attention. These 598 facilities represent a substantial share of Japan's incineration capacity and process a significant portion of the country's municipal waste. They burn that waste and release the thermal energy to the atmosphere, a waste of energy resource that has been characterized in the European WtE literature as ``landfilling in the air'' \citep{EuropeanCommission2017}.

The barriers to adding power generation at existing non-generating facilities are both technical and economic. Technically, many small and old non-generating facilities lack the boiler pressure rating and turbine infrastructure required for electricity generation, and the civil works to retrofit this equipment can approach the cost of new construction. Economically, the scale of waste processing at small facilities is often insufficient to justify the capital investment in power generation infrastructure even at current electricity prices; for facilities processing fewer than 50--70 t/day, the economics of retrofit are generally unfavourable regardless of facility age. These are two distinct constraints, architectural and economic, and they reinforce each other: facilities small enough to be unprofitable to retrofit are also typically old enough that the remaining asset life does not justify the investment even if it were technically straightforward.

An illustrative break-even calculation sharpens this point. A representative non-generating facility processing approximately 100 t/day of waste (at typical post-2010 utilisation of 75\%, roughly 27{,}000 tonnes per year) would, if retrofitted to operate at the efficiency of a 20-year-old power-generating facility of similar scale (approximately 0.20 MWh/t, the middle of the range estimated in Table~\ref{tab:efficiency_age}), produce on the order of 5{,}400 MWh of electricity annually. Retrofit costs for adding boiler pressure upgrades, a small steam turbine, and grid-connection infrastructure to an existing stoker furnace are not standardised in the public Japanese literature, but engineering-handbook ranges place them at roughly 30--60\% of the capital cost of a new facility of equivalent generating capacity \citep{Niessen2010}, which for a 100 t/day facility corresponds to on the order of two to four billion yen. At the FY2024 feed-in-tariff level for biomass-classified waste of roughly 15--17 yen per kWh, annual electricity revenue would reach approximately 80--90 million yen, implying a simple payback period well in excess of twenty years for the upper end of the cost range, longer than the residual economic lifetime of the ageing facilities at which retrofit is most needed. The calculation is deliberately crude: it omits operations and maintenance costs, salvage value, and steam-sale revenue (which is close to zero for most Japanese facilities, for the institutional reasons set out earlier in the discussion of heat integration). But even with these omissions, it illustrates why the observed non-conversion of the non-generating segment is not a puzzle.

The same calculation can be used to estimate the break-even carbon price at which retrofit would dominate replacement. At a carbon price of approximately 3{,}000 yen per tonne of CO$_2$, close to the starter level of Japan's GX-ETS introduced in 2023, the additional value of avoided emissions (5{,}400 MWh $\times$ 0.49 t-CO$_2$/MWh $\times$ 3{,}000 yen/t $\approx$ 8 million yen per year) is a trivial contribution that does not move the payback period materially. For retrofit economics to become compelling for the small, old, non-generating segment, the carbon price would need to reach the order of 20{,}000--30{,}000 yen per tonne of CO$_2$ \emph{and} be committed for a horizon long enough to justify the capital expenditure, a combination Japan's current carbon pricing architecture does not promise. This back-of-envelope exercise gives the ``unlikely under foreseeable economics'' claim its quantitative content: the break-even carbon price for retrofitting small old facilities is materially above any price Japan is currently considering, and the robustness of the conclusion to plausible variation in the cost and revenue parameters is what distinguishes this argument from a simple assertion of infeasibility.

The policy implication is therefore that the non-generating segment is unlikely to be converted to generating in place at meaningful scale under current or foreseeable economic conditions; at fleet scale, major capital modernisation appears more feasible than diffuse retrofit of the small, old, non-generating segment. This claim is weaker than ``impossible'' and stronger than ``merely expensive'': it reflects the combined structure of architectural and economic barriers documented above, together with the empirical observation from the panel that such conversions have not occurred at meaningful scale over the 20-year study period even when the Fukushima shock raised the marginal return to electricity generation. And because facility-level capital renewal without regional consolidation simply perpetuates the fragmented structure that limits scale economies, any modernization strategy must be coordinated at the regional level. This is, again, a governance challenge more than a technical one.

\subsubsection{Waste-to-Energy in the Circular Economy Hierarchy}

A legitimate question from the circular economy perspective is whether improving WtE efficiency is the right goal, or whether policy energy should instead be directed toward reducing the waste streams that require incineration in the first place. This thesis does not take a position on the relative priority of waste reduction, reuse, recycling, and energy recovery, that is a broader question about Japan's material economy that extends well beyond the scope of this analysis. What the thesis does contribute is a clearer picture of the energy recovery tier as it currently exists: highly heterogeneous, partially modernized, and constrained by design decisions made decades ago.

Within the tier of residual waste that requires thermal treatment, waste that cannot be economically recycled and would otherwise require landfilling, the evidence is clear that modern, large-scale WtE is substantially more efficient than old, small-scale incineration. To the extent that Japan will continue to manage residual waste through incineration (and all demographic and policy projections suggest it will, for the foreseeable future), the findings of this thesis are unambiguous about the direction of improvement: larger, newer, and more fully utilized.

\subsection{Limitations}

\subsubsection{Data Limitations}

The analysis depends on the accuracy and completeness of the General Waste Treatment Survey, which is an administrative dataset subject to the reporting conventions and potential errors of prefectural and municipal administrators. While the survey is near-census in coverage, systematic reporting biases, for example, if municipalities with low-performing facilities are more likely to under-report efficiency metrics, could bias the regression estimates. The analysis can partially address this concern through the robustness checks, but cannot fully rule it out without access to independently verified facility-level data.

Heating value is an estimated rather than measured variable, as described in Section 3.3.3. The null result on heating value may partly reflect measurement error rather than (or in addition to) a genuine absence of effect. More precise waste composition monitoring would allow this question to be revisited.

\subsubsection{Causal Identification}

The regression analysis identifies conditional correlations between facility characteristics and efficiency, associations that are stable across model specifications, consistent with theoretical priors, and robust to multiple specification choices. However, causal identification in the strict econometric sense requires either random variation in treatment (which does not exist for facility age or design capacity) or a valid instrumental variable (which this thesis does not employ).

The age coefficient, in particular, should be interpreted as reflecting the combined effect of design vintage and physical ageing, two mechanisms that are observationally equivalent in this data. The within-facility variation analysis provides indirect descriptive evidence that vintage rather than degradation is the dominant mechanism, and that within-facility responsiveness is bounded in the canonical generator sample, but it does not by itself uniquely identify physical lock-in relative to retrofit history, governance constraints, or other omitted channels. Direct identification of the vintage effect would require data on facility design specifications at construction, data that are not available in the General Waste Treatment Survey.

\subsubsection{External Validity}

The findings pertain specifically to Japan's municipal waste incineration fleet, which has characteristics that may not generalize to WtE contexts in other countries: predominantly stoker furnace technology, municipal ownership, very limited district heating integration, and heterogeneous waste composition. The scale of the age effect, in particular, may differ in contexts where facility design has evolved differently or where maintenance regimes are more intensive.

Within Japan, the findings are based on fiscal years 2005--2024 and reflect the conditions of that period. Future changes in waste composition (particularly changes in plastic content following recent packaging regulations), energy market structure (as renewable energy penetration increases and the grid emission factor continues to decline), or facility technology (if new combustion or gasification technologies gain market share) could alter the efficiency relationships estimated here.

%% ==========================================================
%% CHAPTER 6: CONCLUSION
%% ==========================================================

\section{Conclusion}

\subsection{Summary of Findings}

This thesis set out to answer a two-part empirical question: what predicts observed transition into power generation among coded facilities first seen without it, and conditional on power generation, what predicts energy recovery efficiency among power-generating incinerators? The analysis, drawing on 23,599 facility-year observations from the Ministry of the Environment's General Waste Treatment Survey (FY2005--FY2024), produces findings that are both empirically robust and theoretically consequential.

The first finding concerns modernization on the extensive margin. In the coded full-fleet panel, 141 observed first-adoption events occur among 2,035 facilities first observed without power generation, and those events are concentrated among young and large facilities. In the lagged adoption model, facilities older than 10 years in the prior observed year are roughly 1.5--2.2 percentage points less likely to adopt power generation in the current year, while each additional 100 t/day of prior-year design capacity raises annual first-adoption probability by about 1.5 percentage points. The coded panel therefore does not show widespread late conversion of old small plants. Instead, observed transition into generation is concentrated among facilities that were already younger and larger before transition, a pattern consistent with capital-side modernization pressure but not by itself sufficient to distinguish retrofit from replacement or new build.

The second finding concerns efficiency conditional on adoption. Three determinants of generator efficiency are established with high confidence across the four main specifications and all eight robustness specifications. Facility age reduces efficiency by approximately 1.9--3.5\% per year in the main models, with stronger penalties appearing in several robustness splits, and mean efficiency declines monotonically from 0.400 MWh/t among facilities aged 0--10 years to 0.183 MWh/t among facilities over 30 years old. Design capacity improves efficiency in every main specification, reflecting the engineering economics of boiler and turbine systems at scale. Capacity utilization also improves efficiency in every main and robustness specification, reflecting thermodynamic gains from operating near design conditions.

Two variables fail to predict efficiency. Waste heating value is statistically insignificant in every specification, suggesting that waste composition management is not a reliable lever for improving energy recovery. Grid emission factors produce sign-unstable coefficients that reverse when year fixed effects are included, indicating that this variable proxies for time trends rather than a genuine causal mechanism.

The deepest conditional finding of the study, however, is not a regression coefficient. The within-facility variation ratio of 0.1499 in the canonical generator frame, and the fact that the ratio remains low across pre-Fukushima (0.1795) and post-Fukushima (0.0956) subsamples, indicates that within the power-generating sample efficiency is much more heterogeneous across facilities than it is within facilities over time. Together with the bounded Fukushima response, this pattern is strongly consistent with bounded infrastructural responsiveness: operational adjustments matter, but they appear too small to erase design- and vintage-based differences once a facility is already in the generating regime.

At the fleet level, Japan's incineration sector has experienced meaningful change over the study period: facility count has fallen 23\% (from 1,318 to 1,014 facilities), and the power-generating share has nearly doubled (from 21.6\% to 41.1\%). Gross avoided CO$_2$ emissions from waste-to-energy reached approximately 4.6 million t-CO$_2$ in FY2024 (an upper bound, as process emissions from combustion are not deducted). But 59\% of active facilities still generate no electricity, and the efficiency gains of the modernizing segment are concentrated in a small number of large, modern plants, a pattern that is simultaneously encouraging (the transition is occurring) and concerning (it is occurring too slowly and unevenly for net-zero compatibility).

\subsection{Theoretical Contributions}

This thesis makes two contributions to the industrial ecology literature. First, it shows that the transition question in Japan's incineration fleet is empirically two-part. The fleet-level movement into power generation is an extensive-margin process concentrated among younger and larger facilities, while the efficiency differences among generators are a separate intensive-margin problem. That distinction is analytically useful beyond this case because infrastructure transitions often blur adoption and performance into one narrative, even when they are driven by different mechanisms.

Second, it provides facility-level evidence strongly consistent with bounded infrastructural lock-in within the generating segment. \citet{Seto2016}, in their synthesis of the post-Unruh lock-in literature, explicitly called for empirical studies that operationalise infrastructural lock-in at the level of individual facilities rather than at the aggregate sectoral scale typical of most lock-in discussions. The low within-facility efficiency variation documented here, measured on 5,683 observations across 1,016 clustered facilities in the canonical power-generating frame and remaining low across the pre- and post-Fukushima subsamples, answers that call in a qualified but important sense: it provides facility-level evidence strongly consistent with the claim that physical infrastructure embeds design decisions in ways that are difficult to reverse through operational means, and that these constraints persist even under dramatic changes in the external incentive environment. The Fukushima period does produce a measurable but bounded attenuation of the age coefficient, which is compatible with a lock-in interpretation: facility-level performance responds to incentives, but within an envelope set by the original design. This enriches the lock-in literature by documenting the pattern in a non-energy-generation context, and is convergent with recent facility-level evidence from China's incinerator fleet \citep{Cui2026}, where vintage cohort is similarly identified as the primary driver of regional performance differences.

\subsection{Policy Recommendations}

The findings support four policy recommendations for Japan's waste management sector as it navigates the path to carbon neutrality.

\textbf{First, accelerate targeted retirement of pre-1995 non-power-generating facilities.} The FY2024 cross-section of the dataset contains approximately 277 such facilities: old enough to face replacement cycles in any case, but burning waste with no energy recovery in the meantime. National subsidies for early retirement, potentially tied to regional consolidation plans that route waste to modern facilities, would bring the transition timeline closer to net-zero compatibility. The data show that the efficiency benefit of replacing a 1985-vintage 80 t/day facility with a 2024-vintage 200 t/day facility is approximately twofold, a gain larger than the bounded operating-side improvements observed in the power-generating sample.

\textbf{Second, scale regional consolidation planning from municipal to prefecture level.} The current municipality-by-municipality approach to facility planning perpetuates a fragmented structure that prevents the scale economies the regression results identify as a primary efficiency driver. Prefecture-level waste management plans that identify optimal facility locations, sizes, and inter-municipal waste routing arrangements, backed by national government coordination grants, would unlock the scale premium currently inaccessible within municipal boundaries.

\textbf{Third, redesign monitoring to serve fleet planning rather than facility auditing.} The finding that within-facility efficiency changes only modestly relative to between-facility gaps means that annual facility-level efficiency monitoring, by itself, provides limited leverage for operational performance management. The same monitoring data, reframed as a fleet vintage register and retirement calendar, would serve the consolidation planning agenda far more effectively, while still supporting routing and utilization improvements within the already-generating segment. The Ministry of the Environment should be resourced to develop and maintain such a register.

\textbf{Fourth, concentrate WtE capital and construction incentives on high-efficiency capital modernisation.} Because the within-facility variation analysis suggests that operating-side incentives are unlikely to close large vintage gaps on their own, financial support should be targeted primarily at \emph{capital decisions that reset the design envelope}, whether replacement or major refurbishment, while preserving scope for selective retrofit where the technical upside is documented. Capital grants, concessional financing, and long-term power purchase agreements structured to reward projected lifetime energy recovery per tonne (rather than flat per-kWh subsidies for facilities already operating) would push the next generation of modernized facilities toward the performance ceiling and accelerate the shift of the fleet's economic center of gravity toward the high-performing segment.

\subsection{Directions for Future Research}

This thesis opens several lines of future inquiry. The most important is the governance of regional consolidation: what institutional arrangements, financial, contractual, political, have successfully enabled inter-municipal coordination in waste management, and which have failed? Case study analysis of successful regional consolidations in Japan would complement the statistical findings here with process understanding.

A second direction concerns the district heating question. Japan's major urban areas, particularly Sapporo and other Hokkaido cities, where winter heating demand is large, may offer underexplored opportunities for combined heat and power from waste incineration, analogous to the Nordic model. District heating integration could substantially increase total energy recovery even from existing facilities, potentially altering the efficiency landscape in ways the current analysis, which focuses only on electricity generation, cannot capture.

Third, the fixed-design finding raises a question about when and whether facility retrofits, major upgrades to boiler systems, turbine replacement, or combustion control modernization, are capable of partially overcoming the design constraint. The current dataset does not contain information on retrofit investments; a supplementary survey of facility modification histories would allow this question to be addressed directly.

Finally, as Japan's renewable energy penetration increases and the grid emission factor continues to decline, the avoided emissions value of waste-to-energy electricity generation will fall. Future work should model the trajectory of WtE's climate benefit under different decarbonization scenarios, to assess at what point the marginal contribution of WtE electricity to avoided emissions falls below the threshold that would justify continued investment in the sector.

\subsection{Closing Statement}

Japan built an incineration fleet for an era when burning waste was the best available option; the question its net-zero commitment now poses is not whether to change that fleet, but how quickly the country can replace what it has already locked in.

%% ==========================================================
%% BIBLIOGRAPHY
%% ==========================================================

\begin{thebibliography}{99}

\bibitem[Arthur(1989)]{Arthur1989}
Arthur, W.~B. (1989).
Competing technologies, increasing returns, and lock-in by historical events.
\emph{The Economic Journal}, \emph{99}(394), 116--131.
\url{https://doi.org/10.2307/2234208}

\bibitem[Astrup et al.(2009)]{Astrup2009}
Astrup, T., M{\o}ller, J., \& Fruergaard, T. (2009).
Incineration and co-combustion of waste: Accounting of greenhouse gases and global warming contributions.
\emph{Waste Management \& Research}, \emph{27}(8), 789--799.
\url{https://doi.org/10.1177/0734242X09343774}

\bibitem[Astrup et al.(2015)]{Astrup2015}
Astrup, T.~F., Tonini, D., Turconi, R., \& Boldrin, A. (2015).
Life cycle assessment of thermal waste-to-energy technologies: Review and recommendations.
\emph{Waste Management}, \emph{37}, 104--115.
\url{https://doi.org/10.1016/j.wasman.2014.06.011}

\bibitem[Ayres \& Simonis(1994)]{Ayres1994}
Ayres, R.~U., \& Simonis, U.~E. (Eds.). (1994).
\emph{Industrial metabolism: Restructuring for sustainable development}.
United Nations University Press.
Retrieved from \url{https://archive.unu.edu/unupress/unupbooks/80841e/80841E00.htm}

\bibitem[Beylot et al.(2015)]{Beylot2015}
Beylot, A., Vaxelaire, S., Zdanevitch, I., Auvinet, N., \& Villeneuve, J. (2015).
Life cycle assessment of mechanical biological pre-treatment of municipal solid waste: A case study.
\emph{Waste Management}, \emph{39}, 287--294.
\url{https://doi.org/10.1016/j.wasman.2015.01.037}

\bibitem[Caldecott et al.(2016)]{Caldecott2016}
Caldecott, B., Harnett, E., Cojoianu, T., Kok, I., \& Pfeiffer, A. (2016).
\emph{Stranded assets: A climate risk challenge}.
Inter-American Development Bank.
Retrieved from \url{https://publications.iadb.org/en/stranded-assets-climate-risk-challenge}

\bibitem[Cui et al.(2026)]{Cui2026}
Cui, J., Cui, Y., Li, J., Gao, X., Wei, W., Chen, Y., Ma, W., Zhu, N., Geng, Y., Zhao, Y., \& Lou, Z. (2026).
Efficiency hierarchy and optimization of waste incineration in China to balance disposal and energy supply.
\emph{Nature Communications}, \emph{17}(1), Article 3069.
\url{https://doi.org/10.1038/s41467-026-69897-w}

\bibitem[Ellen MacArthur Foundation(2013)]{EllenMacArthur2013}
Ellen MacArthur Foundation. (2013).
\emph{Towards the circular economy: Economic and business rationale for an accelerated transition}.
Ellen MacArthur Foundation.
Retrieved from \url{https://www.ellenmacarthurfoundation.org/towards-the-circular-economy-vol-1-an-economic-and-business-rationale-for-an}

\bibitem[European Commission(2017)]{EuropeanCommission2017}
European Commission. (2017).
\emph{The role of waste-to-energy in the circular economy} (COM(2017) 34 final).
European Commission.
Retrieved from \url{https://eur-lex.europa.eu/legal-content/EN/TXT/?uri=CELEX:52017DC0034}

\bibitem[Geels(2004)]{Geels2004}
Geels, F.~W. (2004).
From sectoral systems of innovation to socio-technical systems: Insights about dynamics and change from sociology and institutional theory.
\emph{Research Policy}, \emph{33}(6--7), 897--920.
\url{https://doi.org/10.1016/j.respol.2004.01.015}

\bibitem[Genon \& Brizio(2008)]{Genon2008}
Genon, G., \& Brizio, E. (2008).
Perspectives and limits for cement kilns as a destination for RDF.
\emph{Waste Management}, \emph{28}(11), 2375--2385.
\url{https://doi.org/10.1016/j.wasman.2007.10.022}

\bibitem[Ministry of the Environment Japan(2022)]{MOEJ2022}
Ministry of the Environment Japan. (2022).
\emph{General waste treatment survey: Summary report FY2021}.
Environmental Management Bureau, Ministry of the Environment Japan.
Retrieved from \url{https://www.env.go.jp/recycle/waste_tech/ippan/r3/index.html}

\bibitem[Ministry of the Environment Japan(2024)]{MOEJ2024}
Ministry of the Environment Japan. (2024).
\emph{Greenhouse gas inventory report of Japan}.
Ministry of the Environment Japan.
Retrieved from \url{https://cger.nies.go.jp/publications/report/i170/en/}

\bibitem[M\"{u}nster \& Meibom(2010)]{Munster2010}
M\"{u}nster, M., \& Meibom, P. (2010).
Long-term affected energy products of waste to energy, a consequential approach.
\emph{Waste Management}, \emph{30}(12), 2510--2519.
\url{https://doi.org/10.1016/j.wasman.2010.04.015}

\bibitem[Niessen(2010)]{Niessen2010}
Niessen, W.~R. (2010).
\emph{Combustion and incineration processes: Applications in environmental engineering} (4th ed.).
CRC Press.
Retrieved from \url{https://www.taylorfrancis.com/books/mono/10.1201/EBK1439805039/combustion-incineration-processes-walter-niessen}

\bibitem[Rausch(2006)]{Rausch2006}
Rausch, A. (2006).
The Heisei Dai Gappei: A case study for understanding the municipal mergers of the Heisei era.
\emph{Japan Forum}, \emph{18}(1), 133--156.
\url{https://doi.org/10.1080/09555800500498558}

\bibitem[Sakai et al.(2008)]{Sakai2008}
Sakai, S., Ikematsu, T., Hirai, Y., \& Yoshida, H. (2008).
Unit-charging programs for municipal solid waste in Japan.
\emph{Waste Management}, \emph{28}(12), 2815--2825.
\url{https://doi.org/10.1016/j.wasman.2008.07.010}

\bibitem[Sakai et al.(2011)]{Sakai2011}
Sakai, S., Yoshida, H., Hirai, Y., Asari, M., Takigami, H., Takahashi, S., Tomoda, K., Peeler, M.~V., Wejchert, J., Schmid-Unterseh, T., Douvan, A.~R., Hathaway, R., Hylander, L.~D., Fischer, C., Oh, G.~J., Jinhui, L., \& Chi, N.~K. (2011).
International comparative study of 3R and waste management policy developments.
\emph{Journal of Material Cycles and Waste Management}, \emph{13}(2), 86--102.
\url{https://doi.org/10.1007/s10163-011-0009-x}

\bibitem[Sasakawa Peace Foundation USA(2012)]{SasakawaPF2012}
Sasakawa Peace Foundation USA. (2012).
\emph{The Fukushima nuclear accident and crisis management: Lessons for Japan-U.S. alliance cooperation}.
Sasakawa Peace Foundation.
Retrieved from \url{https://spfusa.org/publications/the-fukushima-nuclear-accident-and-crisis-management/}

\bibitem[Seto et al.(2016)]{Seto2016}
Seto, K.~C., Davis, S.~J., Mitchell, R.~B., Stokes, E.~C., Unruh, G., \& {\"U}rge-Vorsatz, D. (2016).
Carbon lock-in: Types, causes, and policy implications.
\emph{Annual Review of Environment and Resources}, \emph{41}(1), 425--452.
\url{https://doi.org/10.1146/annurev-environ-110615-085934}

\bibitem[Sun et al.(2018)]{Sun2018}
Sun, L., Fujii, M., Tasaki, T., Dong, H., \& Ohnishi, S. (2018).
Improving waste to energy rate by promoting an integrated municipal solid-waste management system.
\emph{Resources, Conservation and Recycling}, \emph{136}, 289--296.
\url{https://doi.org/10.1016/j.resconrec.2018.05.005}

\bibitem[Tabata \& Tsai(2016)]{TabataTsai2016}
Tabata, T., \& Tsai, P. (2016).
Heat supply from municipal solid waste incineration plants in Japan: Current situation and future challenges.
\emph{Waste Management \& Research}, \emph{34}(4), 345--351.
\url{https://doi.org/10.1177/0734242X15617009}

\bibitem[Tanikawa et al.(2015)]{Tanikawa2015}
Tanikawa, H., Fishman, T., Okuoka, K., \& Sugimoto, K. (2015).
The weight of society over time and space: A comprehensive account of the construction material stock of Japan, 1945--2010.
\emph{Journal of Industrial Ecology}, \emph{19}(5), 778--791.
\url{https://doi.org/10.1111/jiec.12284}

\bibitem[Unruh(2000)]{Unruh2000}
Unruh, G.~C. (2000).
Understanding carbon lock-in.
\emph{Energy Policy}, \emph{28}(12), 817--830.
\url{https://doi.org/10.1016/S0301-4215(00)00070-7}

\bibitem[Wooldridge(2010)]{Wooldridge2010}
Wooldridge, J.~M. (2010).
\emph{Econometric analysis of cross section and panel data} (2nd ed.).
MIT Press.
Retrieved from \url{https://mitpress.mit.edu/9780262232586/econometric-analysis-of-cross-section-and-panel-data/}

\bibitem[Yamada et al.(2023)]{Yamada2023}
Yamada, K., Ii, R., Yamamoto, M., Ueda, H., \& Sakai, S. (2023).
Japan's greenhouse gas reduction scenarios toward net zero by 2050 in the material cycles and waste management sector.
\emph{Journal of Material Cycles and Waste Management}, \emph{25}(4), 1807--1823.
\url{https://doi.org/10.1007/s10163-023-01650-7}

\end{thebibliography}

\end{document}
